---
title: "Stage 3 Pilot Analysis — Sponsorship Network"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    code_folding: hide
    fig_width: 10
    fig_height: 6
  pdf_document:
    toc: true
    fig_caption: true
    latex_engine: pdflatex
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6
)

library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)

# kableExtra for HTML only — tabu package bug breaks PDF in this TeX distro
is_pdf <- knitr::is_latex_output()
if (!is_pdf) library(kableExtra)

# Wrapper: uses kableExtra styling for HTML, plain booktabs for PDF
styled_kable <- function(data, ...) {
  k <- kable(data, booktabs = TRUE, ...)
  if (!is_pdf) k <- kable_styling(k, bootstrap_options = c("striped", "condensed"), full_width = FALSE)
  k
}

# Penn colors
PENN_BLUE   <- "#011F5B"
PENN_RED    <- "#990000"
SUCCESS_GRN <- "#2E7D32"
FAILURE_RED <- "#C62828"

# Target study ID
TARGET_STUDY <- "698e27db580428e78f8e9ff1"
```

# Overview

This is the pilot analysis for **Stage 3** of the Sponsorship Network experiment (Study `r TARGET_STUDY`). Stage 3 evaluators see endorsements from real Stage 2 endorsers, then stake a portion of a \$2 bonus on whether the endorser was correct.

**Design:** 2 x 2 x 2 between-subjects factorial

- **Endorser Gender** (Man vs. Woman)
- **Endorser Correctness** (Correct vs. Incorrect on Q1)
- **Endorsement Strength** (Strong vs. Weak — distance from neutral 50)

**Primary DV:** Stake percentage (0–100%) on endorser being correct

**Research Questions:**

| RQ | Question | DV |
|:---|:---------|:---|
| RQ1 | Are female sponsors punished more for failures / rewarded less for successes? | Trust Change (Q2 - Q1) |
| RQ2 | Do female sponsors provide weaker endorsements? | Abs. Endorsement Strength |
| RQ3 | Do female sponsors need higher strength to achieve same initial trust? | Q1 Stake |
| RQ4 | Is trust change more contingent on strength x outcome for females? | Trust Change (Q2 - Q1) |

\newpage

# 1. Data Loading & Cleaning

## 1.1 Load Raw Export

```{r load-data}
raw <- read.csv("../output/stage3_pilot_data.csv", stringsAsFactors = FALSE)

# Qualtrics exports 3 header rows: labels (row 1), descriptions (row 2), import IDs (row 3)
header_labels <- raw[1, ]
raw <- raw[-c(1, 2), ]  # drop label + importId rows

# Convert numeric fields
numeric_cols <- c("Progress", "Duration..in.seconds.", "Finished",
                  "endorser_slider_value_q1", "endorser_slider_value_q2",
                  "stake_percent_q1", "stake_percent_q2",
                  "rt_ms_stage3_q1", "rt_ms_stage3_q2", "rt_ms_stage3_outcome",
                  "stage3_q1_is_correct", "stage3_q1_actual_bonus",
                  "age", "gender", "race")

for (col in numeric_cols) {
  if (col %in% names(raw)) {
    raw[[col]] <- suppressWarnings(as.numeric(raw[[col]]))
  }
}

raw$StartDate <- as.POSIXct(raw$StartDate, format = "%Y-%m-%d %H:%M:%S")
raw$EndDate   <- as.POSIXct(raw$EndDate, format = "%Y-%m-%d %H:%M:%S")

cat("Total rows in export:", nrow(raw), "\n")
```

## 1.2 Exclusion Cascade

Participants must pass ALL of the following filters:

1. **Not a preview** (Status != 1)
2. **Completed survey** (Finished == 1)
3. **Valid Prolific participant** (PROLIFIC_PID is non-empty)
4. **Passed comprehension check** (Q42 == 2: correctly identified endorser information access)
5. **Has condition assignment** (JS ran successfully, assigned_condition non-empty)
6. **Has Q1 stake data** (stake_percent_q1 recorded)

```{r exclusion-cascade}
# Build exclusion funnel
funnel <- data.frame(
  Step = character(),
  Remaining = integer(),
  Excluded = integer(),
  stringsAsFactors = FALSE
)

add_step <- function(funnel, name, data) {
  prev_n <- if (nrow(funnel) == 0) nrow(raw) else funnel$Remaining[nrow(funnel)]
  funnel <- rbind(funnel, data.frame(
    Step = name,
    Remaining = nrow(data),
    Excluded = prev_n - nrow(data),
    stringsAsFactors = FALSE
  ))
  return(funnel)
}

d0 <- raw
funnel <- add_step(funnel, "Total export rows", d0)

d1 <- d0 %>% filter(Status != "1")
funnel <- add_step(funnel, "Exclude preview responses", d1)

d2 <- d1 %>% filter(Finished == 1)
funnel <- add_step(funnel, "Exclude incomplete", d2)

d3 <- d2 %>% filter(!is.na(PROLIFIC_PID) & trimws(PROLIFIC_PID) != "")
funnel <- add_step(funnel, "Require valid PROLIFIC_PID", d3)

d3b <- d3 %>% filter(STUDY_ID == TARGET_STUDY)
funnel <- add_step(funnel, paste0("Match target study (", TARGET_STUDY, ")"), d3b)

d4 <- d3b %>% filter(Q42 == "2")
funnel <- add_step(funnel, "Pass comprehension check (Q42=2)", d4)

d5 <- d4 %>% filter(!is.na(assigned_condition) & trimws(assigned_condition) != "")
funnel <- add_step(funnel, "Has condition assignment (JS ran)", d5)

d6 <- d5 %>% filter(!is.na(stake_percent_q1))
funnel <- add_step(funnel, "Has Q1 stake data", d6)

df <- d6

styled_kable(funnel, col.names = c("Filter Step", "N Remaining", "N Excluded"))

cat("\nFinal analytic sample: N =", nrow(df), "\n")
```

## 1.3 Derive Variables

```{r derive-variables}
df <- df %>%
  mutate(
    # Extract factors from assigned_condition (e.g., "M_correct_strong")
    endorser_gender_code = ifelse(grepl("^M_", assigned_condition), "Man", "Woman"),
    endorser_correct     = ifelse(grepl("_correct_", assigned_condition), 1, 0),
    endorser_strong      = ifelse(grepl("_strong$", assigned_condition), 1, 0),

    # Compute absolute endorsement strength (distance from neutral 50)
    abs_strength_q1 = abs(endorser_slider_value_q1 - 50),
    abs_strength_q2 = abs(endorser_slider_value_q2 - 50),

    # Factor versions for modeling
    endorser_gender_f = factor(endorser_gender_code, levels = c("Man", "Woman")),
    correctness_f     = factor(ifelse(endorser_correct == 1, "Correct", "Incorrect"),
                               levels = c("Incorrect", "Correct")),
    strength_f        = factor(ifelse(endorser_strong == 1, "Strong", "Weak"),
                               levels = c("Weak", "Strong")),
    outcome_f         = factor(ifelse(stage3_q1_is_correct == 1, "Success", "Failure"),
                               levels = c("Failure", "Success")),

    # Trust change = Q2 stake - Q1 stake
    trust_change = stake_percent_q2 - stake_percent_q1,

    # Participant demographics
    participant_gender = case_when(
      gender == 1 ~ "Male",
      gender == 2 ~ "Female",
      gender == 3 ~ "Other/Non-binary",
      TRUE ~ NA_character_
    ),

    # Duration in minutes
    duration_min = Duration..in.seconds. / 60
  )

n_q2     <- sum(!is.na(df$trust_change))
n_rt     <- sum(df$rt_ms_stage3_q1 > 0, na.rm = TRUE)
n_conds  <- length(unique(df$assigned_condition))

cat("Derived variables created.\n")
cat("  Total valid N:", nrow(df), "\n")
cat("  Trust change computable (has Q2):", n_q2, "/", nrow(df), "\n")
cat("  Response times recorded:", n_rt, "/", nrow(df), "\n")
cat("  Conditions covered:", n_conds, "/ 8\n")
```

\newpage

# 2. Data Quality & Diagnostics

## 2.1 Response Overview

```{r response-overview}
overview <- data.frame(
  Metric = c(
    "Total export rows",
    "Final analytic sample",
    "Q1 stake recorded",
    "Q2 stake recorded",
    "Trust change computable",
    "Response times recorded (Q1)",
    "Conditions covered (of 8)",
    paste0("From target study (", TARGET_STUDY, ")")
  ),
  Value = c(
    nrow(raw),
    nrow(df),
    sum(!is.na(df$stake_percent_q1)),
    sum(!is.na(df$stake_percent_q2)),
    n_q2,
    n_rt,
    n_conds,
    sum(df$STUDY_ID == TARGET_STUDY, na.rm = TRUE)
  )
)

styled_kable(overview, align = "lr")
```

## 2.2 Comprehension Check Breakdown

Q42 asks: *"When the endorsers made their predictions, what information did they have access to?"*

- Choice 1: "Only the candidates' logical-reasoning test scores"
- **Choice 2 (CORRECT): "The candidates' knowledge quiz and/or word-search puzzle scores (some may have been listed as 'Unknown')"**
- Choice 3: "All three task scores: logical-reasoning, knowledge quiz, and word-search"
- Choice 4: "The candidates' names and demographics"

This is a **hard gate** in the survey — incorrect answers end the survey with redirect code `C100PIGA`. We still document it here for transparency.

```{r comprehension-check}
# Among all Prolific participants who completed the survey
comp_pool <- raw %>%
  filter(Status != "1", Finished == 1,
         !is.na(PROLIFIC_PID), trimws(PROLIFIC_PID) != "")

comp_tbl <- comp_pool %>%
  count(Q42) %>%
  mutate(
    Label = case_when(
      Q42 == "1" ~ "Only logical-reasoning scores",
      Q42 == "2" ~ "Knowledge quiz / word-search (CORRECT)",
      Q42 == "3" ~ "All three task scores",
      Q42 == "4" ~ "Names and demographics",
      TRUE ~ "No response / screened before Q42"
    ),
    Pct = paste0(round(n / sum(n) * 100, 1), "%")
  )

styled_kable(comp_tbl, col.names = c("Q42 Value", "Label", "N", "%"))
```

## 2.3 Attention Checks (Effort Checks)

```{r attention-checks}
# ec_1 items: bee sting, Thailand, Venus, water, fatal heart attack, human
# Trap items with objectively correct answers:
#   Venus = 2 (No), water = 1 (Yes), fatal heart attack = 2 (No), human = 1 (Yes)

df <- df %>%
  mutate(
    check_venus  = (ec_1_3 == "2"),
    check_water  = (ec_1_4 == "1"),
    check_fatal  = (ec_1_5 == "2"),
    check_human  = (ec_1_6 == "1"),
    check_text   = grepl("^\\\"?one two\\\"?$", tolower(trimws(ec_2))),
    attn_passed  = check_venus & check_water & check_fatal & check_human & check_text,
    n_checks_passed = check_venus + check_water + check_fatal + check_human + check_text
  )

attn_summary <- data.frame(
  Check = c("Venus (never been)", "Water (has drunk)", "Fatal heart attack (no)",
            "Human (yes)", "Text entry ('one two')", "ALL passed"),
  Pass_N = c(sum(df$check_venus, na.rm = TRUE),
             sum(df$check_water, na.rm = TRUE),
             sum(df$check_fatal, na.rm = TRUE),
             sum(df$check_human, na.rm = TRUE),
             sum(df$check_text, na.rm = TRUE),
             sum(df$attn_passed, na.rm = TRUE)),
  Pass_Pct = paste0(round(c(
    mean(df$check_venus, na.rm = TRUE),
    mean(df$check_water, na.rm = TRUE),
    mean(df$check_fatal, na.rm = TRUE),
    mean(df$check_human, na.rm = TRUE),
    mean(df$check_text, na.rm = TRUE),
    mean(df$attn_passed, na.rm = TRUE)
  ) * 100, 1), "%")
)

styled_kable(attn_summary, col.names = c("Check", "N Passed", "% Passed"),
      caption = paste0("Attention checks among final sample (N=", nrow(df), ")"))

cat("\nAttention check failures in final sample:", sum(!df$attn_passed, na.rm = TRUE), "\n")
```

## 2.4 Manipulation Check: Endorser Gender

```{r manip-check}
# Q44: "What is the gender of the endorser?" (1=Man, 2=Woman, 3=I don't remember)
df <- df %>%
  mutate(
    q44_response = case_when(
      Q44 == "1" ~ "Man",
      Q44 == "2" ~ "Woman",
      Q44 == "3" ~ "Don't remember",
      TRUE ~ NA_character_
    ),
    gender_manip_correct = (q44_response == endorser_gender_code)
  )

manip_tbl <- df %>%
  filter(!is.na(q44_response)) %>%
  group_by(endorser_gender_f) %>%
  summarise(
    N = n(),
    Correct = sum(gender_manip_correct, na.rm = TRUE),
    `Don't Remember` = sum(q44_response == "Don't remember", na.rm = TRUE),
    Wrong = N - Correct - `Don't Remember`,
    Accuracy = paste0(round(Correct / N * 100, 1), "%"),
    .groups = "drop"
  )

styled_kable(manip_tbl)

overall_acc <- mean(df$gender_manip_correct, na.rm = TRUE)
cat("\nOverall manipulation check accuracy:", round(overall_acc * 100, 1), "%\n")
if (overall_acc < 0.7) {
  cat("WARNING: Gender manipulation accuracy below 70% — consider strengthening the gender cue.\n")
}
```

## 2.5 Completion Time

```{r duration}
ggplot(df, aes(x = duration_min)) +
  geom_histogram(bins = 20, fill = PENN_BLUE, color = "white", alpha = 0.8) +
  geom_vline(xintercept = median(df$duration_min, na.rm = TRUE),
             linetype = "dashed", color = PENN_RED, size = 1) +
  annotate("text", x = median(df$duration_min, na.rm = TRUE) + 0.3,
           y = Inf, vjust = 2, hjust = 0,
           label = paste0("Median: ", round(median(df$duration_min, na.rm = TRUE), 1), " min"),
           color = PENN_RED, fontface = "bold") +
  labs(title = "Survey Completion Time",
       x = "Duration (minutes)", y = "Count") +
  theme_bw()

cat("Duration stats (minutes):\n")
cat("  Mean:", round(mean(df$duration_min, na.rm = TRUE), 1), "\n")
cat("  Median:", round(median(df$duration_min, na.rm = TRUE), 1), "\n")
cat("  SD:", round(sd(df$duration_min, na.rm = TRUE), 1), "\n")
cat("  Range:", round(min(df$duration_min, na.rm = TRUE), 1), "–",
    round(max(df$duration_min, na.rm = TRUE), 1), "\n")
```

\newpage

# 3. Sample Description

## 3.1 Demographics

```{r demographics}
cat("Age:\n")
cat("  N:", sum(!is.na(df$age)), "\n")
cat("  Mean:", round(mean(df$age, na.rm = TRUE), 1), "\n")
cat("  SD:", round(sd(df$age, na.rm = TRUE), 1), "\n")
cat("  Range:", min(df$age, na.rm = TRUE), "–", max(df$age, na.rm = TRUE), "\n\n")

gender_tbl <- df %>%
  count(participant_gender) %>%
  mutate(Pct = paste0(round(n / sum(n) * 100, 1), "%"))
styled_kable(gender_tbl, col.names = c("Gender", "N", "%"),
      caption = "Participant gender")

race_labels <- c("1" = "AI/AN", "2" = "Asian", "3" = "Black/AA",
                 "4" = "Hispanic/Latino", "5" = "White", "6" = "Other")
race_tbl <- df %>%
  mutate(race_label = ifelse(!is.na(race), race_labels[as.character(race)], "Missing")) %>%
  count(race_label) %>%
  mutate(Pct = paste0(round(n / sum(n) * 100, 1), "%"))
styled_kable(race_tbl, col.names = c("Race/Ethnicity", "N", "%"))
```

## 3.2 Condition Assignment

```{r condition-balance}
cond_tbl <- df %>%
  count(assigned_condition) %>%
  arrange(assigned_condition)

all_conds <- c("M_correct_strong", "M_correct_weak", "M_incorrect_strong",
               "M_incorrect_weak", "W_correct_strong", "W_correct_weak",
               "W_incorrect_strong", "W_incorrect_weak")
cond_tbl <- data.frame(assigned_condition = all_conds) %>%
  left_join(cond_tbl, by = "assigned_condition") %>%
  mutate(n = ifelse(is.na(n), 0, n))

ggplot(cond_tbl, aes(x = reorder(assigned_condition, -n), y = n,
                      fill = ifelse(n == 0, "Empty", "Filled"))) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_text(aes(label = n), vjust = -0.5, fontface = "bold") +
  geom_hline(yintercept = nrow(df) / 8, linetype = "dashed", color = "gray50") +
  scale_fill_manual(values = c("Empty" = "gray80", "Filled" = PENN_BLUE), guide = "none") +
  labs(title = "Condition Assignment (N per cell)",
       subtitle = paste0("Expected per cell: ~", round(nrow(df) / 8, 1),
                         " | Actual range: ", min(cond_tbl$n), "–", max(cond_tbl$n)),
       x = NULL, y = "N") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10))
```

```{r factor-balance}
factor_bal <- data.frame(
  Factor = c("Endorser Gender: Man", "Endorser Gender: Woman",
             "Correctness: Correct", "Correctness: Incorrect",
             "Strength: Strong", "Strength: Weak"),
  N = c(sum(df$endorser_gender_code == "Man"),
        sum(df$endorser_gender_code == "Woman"),
        sum(df$endorser_correct == 1),
        sum(df$endorser_correct == 0),
        sum(df$endorser_strong == 1),
        sum(df$endorser_strong == 0)),
  Pct = paste0(round(c(
    mean(df$endorser_gender_code == "Man"),
    mean(df$endorser_gender_code == "Woman"),
    mean(df$endorser_correct == 1),
    mean(df$endorser_correct == 0),
    mean(df$endorser_strong == 1),
    mean(df$endorser_strong == 0)
  ) * 100, 1), "%")
)

styled_kable(factor_bal, col.names = c("Factor Level", "N", "%"))
```

\newpage

# 4. Primary DVs: Q1 Stake & Trust Change

## 4.1 Q1 Stake Distribution (Initial Trust)

```{r q1-stake-dist}
ggplot(df, aes(x = stake_percent_q1)) +
  geom_histogram(bins = 20, fill = PENN_BLUE, color = "white", alpha = 0.8) +
  geom_vline(xintercept = 50, linetype = "dashed", color = "gray50") +
  geom_vline(xintercept = mean(df$stake_percent_q1, na.rm = TRUE),
             linetype = "solid", color = PENN_RED, size = 1) +
  annotate("text", x = mean(df$stake_percent_q1) + 2, y = Inf, vjust = 2, hjust = 0,
           label = paste0("M = ", round(mean(df$stake_percent_q1), 1)),
           color = PENN_RED, fontface = "bold") +
  scale_x_continuous(breaks = seq(0, 100, 10)) +
  labs(title = "Q1 Stake Distribution (Initial Trust)",
       subtitle = paste0("N = ", nrow(df), " | Mean = ", round(mean(df$stake_percent_q1), 1),
                         " | SD = ", round(sd(df$stake_percent_q1), 1),
                         " | Median = ", median(df$stake_percent_q1)),
       x = "Stake (%)", y = "Count") +
  theme_bw()
```

## 4.2 Trust Change Distribution (Q2 - Q1)

```{r trust-change-dist}
df_tc <- df %>% filter(!is.na(trust_change))

if (nrow(df_tc) > 0) {
  ggplot(df_tc, aes(x = trust_change)) +
    geom_histogram(bins = 20, fill = PENN_BLUE, color = "white", alpha = 0.8) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_vline(xintercept = mean(df_tc$trust_change),
               linetype = "solid", color = PENN_RED, size = 1) +
    annotate("text", x = mean(df_tc$trust_change) + 2, y = Inf, vjust = 2, hjust = 0,
             label = paste0("M = ", round(mean(df_tc$trust_change), 1)),
             color = PENN_RED, fontface = "bold") +
    scale_x_continuous(breaks = seq(-100, 100, 10)) +
    labs(title = "Trust Change Distribution (Q2 Stake - Q1 Stake)",
         subtitle = paste0("N = ", nrow(df_tc), " | Mean = ", round(mean(df_tc$trust_change), 1),
                           " | SD = ", round(sd(df_tc$trust_change), 1),
                           " | Median = ", median(df_tc$trust_change)),
         x = "Trust Change (percentage points)", y = "Count") +
    theme_bw()
} else {
  cat("No trust change data available (Q2 stake missing for all responses).\n")
}

cat("Trust change summary:\n")
cat("  N with Q2:", nrow(df_tc), "/", nrow(df), "\n")
if (nrow(df_tc) > 0) {
  cat("  Mean:", round(mean(df_tc$trust_change), 1), "\n")
  cat("  SD:", round(sd(df_tc$trust_change), 1), "\n")
  cat("  Range:", round(min(df_tc$trust_change), 1), "to",
      round(max(df_tc$trust_change), 1), "\n")
}
```

## 4.3 Q1 vs Q2 Stake (Paired)

```{r q1-q2-paired, fig.height=6}
if (nrow(df_tc) > 2) {
  ggplot(df_tc, aes(x = stake_percent_q1, y = stake_percent_q2)) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray50") +
    geom_point(aes(color = endorser_gender_f), alpha = 0.6, size = 3) +
    geom_smooth(method = "lm", se = TRUE, color = "gray30", alpha = 0.15) +
    scale_color_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
    scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
    scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
    labs(title = "Q1 vs Q2 Stake (Paired within Participant)",
         subtitle = "Points above diagonal = trust increased; below = decreased",
         x = "Q1 Stake (%)", y = "Q2 Stake (%)",
         color = "Endorser Gender") +
    theme_bw() +
    theme(legend.position = "bottom")
}
```

## 4.4 Stake by Condition (All Cells)

```{r stake-by-condition}
cond_stats <- df %>%
  group_by(assigned_condition) %>%
  summarise(
    n = n(),
    q1_mean = round(mean(stake_percent_q1), 1),
    q1_sd = round(sd(stake_percent_q1), 1),
    q2_mean = ifelse(sum(!is.na(stake_percent_q2)) > 0,
                     round(mean(stake_percent_q2, na.rm = TRUE), 1), NA),
    tc_mean = ifelse(sum(!is.na(trust_change)) > 0,
                     round(mean(trust_change, na.rm = TRUE), 1), NA),
    n_q2 = sum(!is.na(stake_percent_q2)),
    .groups = "drop"
  ) %>%
  arrange(assigned_condition)

styled_kable(cond_stats,
      col.names = c("Condition", "N", "Q1 Mean", "Q1 SD",
                     "Q2 Mean", "Trust Change", "N (Q2)"))
```

\newpage

# 5. RQ3: Initial Trust ~ Endorser Gender x Endorsement Strength

**Hypothesis (HQ3):** Female sponsors need **higher** endorsement strength to achieve the same initial trust. Predicts a negative interaction: female endorsers have a shallower slope relating strength to trust.

$$
\text{Stake}_{Q1} = \beta_0 + \beta_1 \text{Female} + \beta_2 \text{AbsStrength} + \beta_3 (\text{Female} \times \text{AbsStrength}) + \epsilon
$$

## 5.1 Model

```{r rq3-model}
model_rq3 <- lm(stake_percent_q1 ~ endorser_gender_f * abs_strength_q1, data = df)
summary(model_rq3)
```

```{r rq3-coefficients}
coefs <- summary(model_rq3)$coefficients
coef_tbl <- data.frame(
  Term = rownames(coefs),
  Estimate = round(coefs[, 1], 3),
  SE = round(coefs[, 2], 3),
  t = round(coefs[, 3], 3),
  p = round(coefs[, 4], 4)
)
rownames(coef_tbl) <- NULL

coef_tbl$Sig <- ifelse(coef_tbl$p < 0.05, "*", "")

styled_kable(coef_tbl, col.names = c("Term", "Estimate", "SE", "t", "p", ""),
      caption = "RQ3 regression coefficients")
```

**Interpretation:**

- `(Intercept)`: Baseline stake for **male** endorsers at **zero** absolute strength
- `endorser_gender_fWoman`: Difference in baseline stake for women vs. men
- `abs_strength_q1`: Slope for males — how much stake increases per unit of endorsement strength
- `endorser_gender_fWoman:abs_strength_q1`: **HQ3 test** — negative = females have shallower slope

## 5.2 Visualization

```{r rq3-scatter, fig.height=6}
ggplot(df, aes(x = abs_strength_q1, y = stake_percent_q1,
               color = endorser_gender_f, fill = endorser_gender_f)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "lm", se = TRUE, alpha = 0.15) +
  scale_color_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_x_continuous(breaks = seq(0, 50, 10), limits = c(0, 50)) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "RQ3: Do Female Endorsers Need Higher Strength for Same Trust?",
    subtitle = paste0("Pilot (N = ", nrow(df), ") | Compare to simulation predictions"),
    x = "Absolute Endorsement Strength (|Slider - 50|)",
    y = "Q1 Stake (%)",
    color = "Endorser Gender", fill = "Endorser Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13)
  )
```

\newpage

# 6. RQ1: Trust Change by Endorser Gender x Outcome

**Hypothesis (HQ1):** Female sponsors are punished **more** for failures and rewarded **less** for successes.

$$
\text{TrustChange} = \beta_0 + \beta_1 \text{Female} + \beta_2 \text{Success} + \beta_3 (\text{Female} \times \text{Success}) + \epsilon
$$

*Requires Q2 stake data. Analysis restricted to participants with both Q1 and Q2.*

```{r rq1-check}
cat("Participants with trust change data:", nrow(df_tc), "\n")
```

## 6.1 Model

```{r rq1-model}
if (nrow(df_tc) >= 10) {
  model_rq1 <- lm(trust_change ~ endorser_gender_f * outcome_f, data = df_tc)
  summary(model_rq1)

  coefs_rq1 <- summary(model_rq1)$coefficients
  coef_tbl_rq1 <- data.frame(
    Term = rownames(coefs_rq1),
    Estimate = round(coefs_rq1[, 1], 3),
    SE = round(coefs_rq1[, 2], 3),
    t = round(coefs_rq1[, 3], 3),
    p = round(coefs_rq1[, 4], 4)
  )
  rownames(coef_tbl_rq1) <- NULL

  coef_tbl_rq1$Sig <- ifelse(coef_tbl_rq1$p < 0.05, "*", "")

  styled_kable(coef_tbl_rq1, col.names = c("Term", "Estimate", "SE", "t", "p", ""),
        caption = "RQ1 regression coefficients")
} else {
  cat("Insufficient data for RQ1 model (need >= 10 with trust change).\n")
}
```

## 6.2 Visualization

```{r rq1-bar, fig.height=5}
if (nrow(df_tc) >= 4) {
  rq1_stats <- df_tc %>%
    group_by(endorser_gender_f, outcome_f) %>%
    summarise(
      n = n(),
      mean_tc = mean(trust_change),
      se = ifelse(n() > 1, sd(trust_change) / sqrt(n()), 0),
      .groups = "drop"
    )

  ggplot(rq1_stats, aes(x = outcome_f, y = mean_tc, fill = endorser_gender_f)) +
    geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
    geom_errorbar(aes(ymin = mean_tc - se, ymax = mean_tc + se),
                  position = position_dodge(0.8), width = 0.25) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_tc, n)),
              position = position_dodge(0.8),
              vjust = ifelse(rq1_stats$mean_tc >= 0, -0.5, 1.5),
              size = 4, fontface = "bold") +
    scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
    labs(
      title = "RQ1: Are Female Sponsors Punished More and Rewarded Less?",
      subtitle = paste0("Trust Change (Q2 - Q1) | N = ", nrow(df_tc)),
      x = "Q1 Outcome", y = "Mean Trust Change (pp)", fill = "Endorser Gender"
    ) +
    theme_bw() +
    theme(legend.position = "bottom",
          plot.title = element_text(size = 14, face = "bold"))
}
```

\newpage

# 7. RQ4: Trust Change ~ Gender x Strength x Outcome (3-Way)

**Hypothesis (HQ4):** Trust change is **more** contingent on endorsement strength x outcome for female sponsors.

$$
\text{TrustChange} = \beta_0 + \beta_1 F + \beta_2 S^c + \beta_3 O + \beta_4 (F \times S^c) + \beta_5 (F \times O) + \beta_6 (S^c \times O) + \beta_7 (F \times S^c \times O) + \epsilon
$$

where $S^c$ = mean-centered absolute strength.

```{r rq4-model}
if (nrow(df_tc) >= 15) {
  df_tc <- df_tc %>%
    mutate(abs_strength_q1_c = abs_strength_q1 - mean(abs_strength_q1, na.rm = TRUE))

  model_rq4 <- lm(trust_change ~ endorser_gender_f * abs_strength_q1_c * outcome_f,
                   data = df_tc)
  summary(model_rq4)
} else {
  cat("Insufficient data for full 3-way interaction (need >= 15).\n")
  cat("Current N with trust change:", nrow(df_tc), "\n")
}
```

## 7.1 Visualization

```{r rq4-scatter, fig.height=6, fig.width=11}
if (nrow(df_tc) >= 8) {
  ggplot(df_tc, aes(x = abs_strength_q1, y = trust_change,
                     color = outcome_f, fill = outcome_f)) +
    geom_point(alpha = 0.5, size = 2.5) +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.15) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    facet_wrap(~ endorser_gender_f, nrow = 1) +
    scale_color_manual(values = c("Failure" = FAILURE_RED, "Success" = SUCCESS_GRN)) +
    scale_fill_manual(values = c("Failure" = FAILURE_RED, "Success" = SUCCESS_GRN)) +
    scale_x_continuous(breaks = seq(0, 50, 10), limits = c(0, 50)) +
    labs(
      title = "RQ4: Is Trust Change More Sensitive to Strength x Outcome for Females?",
      subtitle = paste0("N = ", nrow(df_tc), " | Compare slope divergence across panels"),
      x = "Absolute Endorsement Strength (|Slider - 50|)",
      y = "Trust Change (pp)", color = "Q1 Outcome", fill = "Q1 Outcome"
    ) +
    theme_bw() +
    theme(
      legend.position = "bottom",
      plot.title = element_text(size = 14, face = "bold"),
      strip.text = element_text(size = 13, face = "bold")
    )
}
```

\newpage

# 8. RQ2: Endorsement Strength by Sponsor Gender (Stage 2 Data)

**Hypothesis (HQ2):** Female sponsors provide **weaker** endorsements (~25% less absolute strength) than male sponsors.

$$
\text{AbsStrength}_{ij} = \beta_0 + \beta_1 \text{FemaleSponsor}_{i} + \beta_2 \text{FemaleProtege}_{j} + \beta_3 (\text{FemaleSponsor}_{i} \times \text{FemaleProtege}_{j}) + \epsilon_{ij}
$$

where AbsStrength = |Slider - 50| (0 = neutral, 50 = maximally confident).

*This analysis uses Stage 2 main study data (N = 200 endorsers, 2,000 trial observations).*

## 8.1 Load Stage 2 Data

```{r load-stage2}
s2_raw <- read.csv("../output/stage2_main_data.csv", stringsAsFactors = FALSE)
s2_raw <- s2_raw[-c(1, 2), ]  # Drop Qualtrics label rows

s2_raw$Finished <- as.numeric(s2_raw$Finished)
s2_raw$StartDate <- as.POSIXct(s2_raw$StartDate, format = "%Y-%m-%d %H:%M:%S")
s2_raw$date <- as.Date(s2_raw$StartDate)

# Filter: not preview, completed, valid PID, main study date
s2 <- s2_raw %>%
  filter(Status != "1", Finished == 1,
         !is.na(PROLIFIC_PID) & trimws(PROLIFIC_PID) != "",
         date >= as.Date("2026-02-12")) %>%
  filter(!is.na(t1_slider_value) & trimws(t1_slider_value) != "")

s2$endorser_gender <- case_when(
  s2$gender == "1" ~ "Man",
  s2$gender == "2" ~ "Woman",
  TRUE ~ "Other"
)

cat("Stage 2 main study endorsers:", nrow(s2), "\n")
cat("Gender: Man =", sum(s2$endorser_gender == "Man"),
    "| Woman =", sum(s2$endorser_gender == "Woman"),
    "| Other =", sum(s2$endorser_gender == "Other"), "\n")
```

```{r reshape-stage2}
# Reshape: 10 trials per endorser → long format
s2_long <- data.frame()
for (i in 1:10) {
  p <- paste0("t", i, "_")
  trial_df <- s2 %>%
    select(PROLIFIC_PID, endorser_gender,
           pair_id = !!paste0(p, "pair_id"),
           category = !!paste0(p, "category"),
           truth = !!paste0(p, "truth"),
           truth_gender = !!paste0(p, "truth_gender"),
           A_gender = !!paste0(p, "A_gender"),
           B_gender = !!paste0(p, "B_gender"),
           slider_value = !!paste0(p, "slider_value"),
           slider_side = !!paste0(p, "slider_side"),
           rt_ms = !!paste0(p, "rt_ms")) %>%
    mutate(trial = i)
  s2_long <- rbind(s2_long, trial_df)
}

s2_long$slider_value <- as.numeric(s2_long$slider_value)
s2_long$rt_ms <- as.numeric(s2_long$rt_ms)

# Keep valid trials from Man/Woman endorsers
s2_trials <- s2_long %>%
  filter(!is.na(slider_value), endorser_gender %in% c("Man", "Woman")) %>%
  mutate(
    abs_strength = abs(slider_value - 50),
    endorsed_side = ifelse(slider_value < 50, "A", ifelse(slider_value > 50, "B", "neutral")),
    endorsed_gender = case_when(
      endorsed_side == "A" ~ A_gender,
      endorsed_side == "B" ~ B_gender,
      TRUE ~ NA_character_
    ),
    is_correct = (endorsed_side == truth),
    endorser_gender_f = factor(endorser_gender, levels = c("Man", "Woman")),
    endorsed_gender_f = factor(endorsed_gender, levels = c("Man", "Woman"))
  )

cat("Total trial observations:", nrow(s2_trials), "\n")
cat("Unique endorsers:", n_distinct(s2_trials$PROLIFIC_PID), "\n")
```

## 8.2 Endorsement Strength by Gender

```{r rq2-descriptive}
rq2_summary <- s2_trials %>%
  group_by(endorser_gender_f) %>%
  summarise(
    N_endorsers = n_distinct(PROLIFIC_PID),
    N_trials = n(),
    Mean = round(mean(abs_strength), 1),
    SD = round(sd(abs_strength), 1),
    Median = median(abs_strength),
    .groups = "drop"
  )

styled_kable(rq2_summary,
      col.names = c("Endorser Gender", "N Endorsers", "N Trials",
                     "Mean |Strength|", "SD", "Median"),
      caption = "Absolute endorsement strength by sponsor gender")

# Also show by endorser x protege gender
rq2_cross <- s2_trials %>%
  filter(!is.na(endorsed_gender_f)) %>%
  group_by(endorser_gender_f, endorsed_gender_f) %>%
  summarise(N = n(), Mean = round(mean(abs_strength), 1),
            SD = round(sd(abs_strength), 1), .groups = "drop")

styled_kable(rq2_cross,
      col.names = c("Endorser Gender", "Endorsed Candidate Gender",
                     "N", "Mean |Strength|", "SD"),
      caption = "Strength by endorser and endorsed candidate gender")
```

## 8.3 RQ2 Model

```{r rq2-model}
s2_model_data <- s2_trials %>% filter(!is.na(endorsed_gender_f))
model_rq2 <- lm(abs_strength ~ endorser_gender_f * endorsed_gender_f, data = s2_model_data)
summary(model_rq2)

coefs_rq2 <- summary(model_rq2)$coefficients
coef_tbl_rq2 <- data.frame(
  Term = rownames(coefs_rq2),
  Estimate = round(coefs_rq2[, 1], 3),
  SE = round(coefs_rq2[, 2], 3),
  t = round(coefs_rq2[, 3], 3),
  p = round(coefs_rq2[, 4], 4)
)
rownames(coef_tbl_rq2) <- NULL
coef_tbl_rq2$Sig <- ifelse(coef_tbl_rq2$p < 0.05, "*", "")

styled_kable(coef_tbl_rq2, col.names = c("Term", "Estimate", "SE", "t", "p", ""),
      caption = "RQ2 regression coefficients")
```

**Interpretation:**

- `endorser_gender_fWoman`: Difference in absolute endorsement strength for female vs male sponsors
- `endorsed_gender_fWoman`: Whether endorsing a female candidate changes strength
- Interaction: Whether female sponsors differ specifically when endorsing female candidates

## 8.4 Visualization

```{r rq2-bar, fig.height=5, fig.width=9}
rq2_plot <- s2_trials %>%
  filter(!is.na(endorsed_gender_f)) %>%
  group_by(endorser_gender_f, endorsed_gender_f) %>%
  summarise(n = n(), mean_str = mean(abs_strength),
            se = sd(abs_strength) / sqrt(n()), .groups = "drop")

ggplot(rq2_plot,
       aes(x = endorser_gender_f, y = mean_str, fill = endorsed_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_str - se, ymax = mean_str + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_str, n)),
            position = position_dodge(0.8),
            vjust = 1.5, size = 4.5, color = "white", fontface = "bold") +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED),
                    name = "Endorsed Candidate") +
  scale_y_continuous(limits = c(0, 45), breaks = seq(0, 45, 5)) +
  labs(
    title = "RQ2: Do Female Sponsors Provide Weaker Endorsements?",
    subtitle = paste0("Absolute Endorsement Strength (|Slider - 50|) | N = ",
                      n_distinct(s2_trials$PROLIFIC_PID), " endorsers, ",
                      nrow(s2_trials), " trials"),
    x = "Sponsor Gender",
    y = "Mean Absolute Endorsement Strength"
  ) +
  theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 13))
```

## 8.5 Strength by Candidate Pair Category

```{r rq2-by-category, fig.height=5.5}
cat_stats <- s2_trials %>%
  group_by(category) %>%
  summarise(n = n(), mean_str = mean(abs_strength),
            se = sd(abs_strength) / sqrt(n()),
            accuracy = mean(is_correct, na.rm = TRUE), .groups = "drop") %>%
  arrange(desc(mean_str))

ggplot(cat_stats, aes(x = reorder(category, mean_str), y = mean_str)) +
  geom_bar(stat = "identity", fill = PENN_BLUE, width = 0.7) +
  geom_errorbar(aes(ymin = pmax(0, mean_str - se),
                    ymax = mean_str + se), width = 0.2) +
  geom_text(aes(label = sprintf("%.1f (acc=%.0f%%)", mean_str, accuracy * 100)),
            hjust = -0.05, size = 3.5) +
  scale_y_continuous(limits = c(0, 55), breaks = seq(0, 50, 10)) +
  coord_flip() +
  labs(title = "Endorsement Strength by Candidate Pair Category",
       subtitle = "Higher strength = more confident endorsement | acc = % picking correct answer",
       x = NULL, y = "Mean Absolute Strength") +
  theme_bw()
```

## 8.6 Endorser Accuracy

```{r rq2-accuracy}
acc_tbl <- s2_trials %>%
  filter(endorsed_side != "neutral") %>%
  group_by(endorser_gender_f) %>%
  summarise(
    N = n(),
    Correct = sum(is_correct, na.rm = TRUE),
    Accuracy = paste0(round(mean(is_correct, na.rm = TRUE) * 100, 1), "%"),
    .groups = "drop"
  )

styled_kable(acc_tbl, col.names = c("Endorser Gender", "N Decisions", "N Correct", "Accuracy"),
      caption = "Endorser accuracy (picking the objectively better candidate)")
```

\newpage

# 9. Descriptive Patterns (Full Factorial, Stage 3)

## 9.1 Gender x Correctness on Q1 Stake

```{r factorial-gender-correct, fig.height=5}
gc_stats <- df %>%
  group_by(endorser_gender_f, correctness_f) %>%
  summarise(n = n(), mean_stake = mean(stake_percent_q1),
            se = sd(stake_percent_q1) / sqrt(n()), .groups = "drop")

ggplot(gc_stats, aes(x = correctness_f, y = mean_stake, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_stake - se, ymax = mean_stake + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_text(aes(label = sprintf("%.0f\n(n=%d)", mean_stake, n)),
            position = position_dodge(0.8), vjust = 1.5,
            color = "white", fontface = "bold", size = 4) +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(title = "Q1 Stake by Endorser Gender x Correctness",
       subtitle = "Evaluators don't know correctness at Q1 — reflects condition-level patterns",
       x = "Endorser Correctness (Q1)", y = "Mean Stake (%)", fill = "Endorser Gender") +
  theme_bw() + theme(legend.position = "bottom")
```

## 9.2 Gender x Strength on Q1 Stake

```{r factorial-gender-strength, fig.height=5}
gs_stats <- df %>%
  group_by(endorser_gender_f, strength_f) %>%
  summarise(n = n(), mean_stake = mean(stake_percent_q1),
            se = sd(stake_percent_q1) / sqrt(n()), .groups = "drop")

ggplot(gs_stats, aes(x = strength_f, y = mean_stake, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_stake - se, ymax = mean_stake + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_text(aes(label = sprintf("%.0f\n(n=%d)", mean_stake, n)),
            position = position_dodge(0.8), vjust = 1.5,
            color = "white", fontface = "bold", size = 4) +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(title = "Q1 Stake by Endorser Gender x Endorsement Strength",
       subtitle = "Key RQ3 pattern — does strength matter differently by gender?",
       x = "Endorsement Strength", y = "Mean Stake (%)", fill = "Endorser Gender") +
  theme_bw() + theme(legend.position = "bottom")
```

## 9.3 Full 2x2x2 Heatmap

```{r factorial-heatmap, fig.height=5}
full_stats <- df %>%
  group_by(endorser_gender_f, correctness_f, strength_f) %>%
  summarise(n = n(), mean_stake = mean(stake_percent_q1), .groups = "drop")

all_combos <- expand.grid(
  endorser_gender_f = factor(c("Man", "Woman"), levels = c("Man", "Woman")),
  correctness_f = factor(c("Incorrect", "Correct"), levels = c("Incorrect", "Correct")),
  strength_f = factor(c("Weak", "Strong"), levels = c("Weak", "Strong"))
)
full_stats <- all_combos %>%
  left_join(full_stats, by = c("endorser_gender_f", "correctness_f", "strength_f"))

ggplot(full_stats, aes(x = strength_f, y = correctness_f, fill = mean_stake)) +
  geom_tile(color = "white", size = 1) +
  geom_text(aes(label = ifelse(is.na(n), "---",
                                sprintf("%.0f%%\n(n=%d)", mean_stake, n))),
            size = 4.5, fontface = "bold") +
  facet_wrap(~ endorser_gender_f) +
  scale_fill_gradient2(low = FAILURE_RED, mid = "white", high = SUCCESS_GRN,
                       midpoint = 50, na.value = "gray90",
                       limits = c(0, 100), name = "Mean Stake (%)") +
  labs(title = "Full 2x2x2 Factorial: Mean Q1 Stake",
       x = "Endorsement Strength", y = "Endorser Correctness") +
  theme_bw() +
  theme(strip.text = element_text(size = 13, face = "bold"),
        axis.text = element_text(size = 11))
```

## 9.4 Trust Change Heatmap (for participants with Q2)

```{r factorial-heatmap-tc, fig.height=5}
if (nrow(df_tc) >= 4) {
  tc_stats <- df_tc %>%
    group_by(endorser_gender_f, outcome_f, strength_f) %>%
    summarise(n = n(), mean_tc = mean(trust_change), .groups = "drop")

  tc_combos <- expand.grid(
    endorser_gender_f = factor(c("Man", "Woman"), levels = c("Man", "Woman")),
    outcome_f = factor(c("Failure", "Success"), levels = c("Failure", "Success")),
    strength_f = factor(c("Weak", "Strong"), levels = c("Weak", "Strong"))
  )
  tc_stats <- tc_combos %>%
    left_join(tc_stats, by = c("endorser_gender_f", "outcome_f", "strength_f"))

  ggplot(tc_stats, aes(x = strength_f, y = outcome_f, fill = mean_tc)) +
    geom_tile(color = "white", size = 1) +
    geom_text(aes(label = ifelse(is.na(n), "---",
                                  sprintf("%+.0f\n(n=%d)", mean_tc, n))),
              size = 4.5, fontface = "bold") +
    facet_wrap(~ endorser_gender_f) +
    scale_fill_gradient2(low = FAILURE_RED, mid = "white", high = SUCCESS_GRN,
                         midpoint = 0, na.value = "gray90",
                         name = "Mean Trust\nChange (pp)") +
    labs(title = "Trust Change by Gender x Outcome x Strength",
         subtitle = paste0("N with Q2 data = ", nrow(df_tc)),
         x = "Endorsement Strength", y = "Q1 Outcome") +
    theme_bw() +
    theme(strip.text = element_text(size = 13, face = "bold"))
}
```

\newpage

# 10. Exploratory Analyses

## 10.1 Endorser Confidence and Evaluator Stake

```{r explore-slider-stake, fig.height=5}
ggplot(df, aes(x = endorser_slider_value_q1, y = stake_percent_q1,
               color = endorser_gender_f)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "lm", se = TRUE, alpha = 0.15) +
  geom_vline(xintercept = 50, linetype = "dashed", color = "gray50") +
  scale_color_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_x_continuous(breaks = seq(0, 100, 10)) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(title = "Evaluator Stake vs. Endorser Slider Value (Raw)",
       subtitle = "Slider <50 = favors B, >50 = favors A, 50 = neutral",
       x = "Endorser Slider Value (0-100)", y = "Q1 Stake (%)",
       color = "Endorser Gender") +
  theme_bw() + theme(legend.position = "bottom")
```

## 10.2 Q1 Stake by Candidate Pair

```{r explore-pair-type, fig.height=5}
pair_stats <- df %>%
  group_by(stage3_q1_pair_id) %>%
  summarise(n = n(), mean_stake = mean(stake_percent_q1),
            se = ifelse(n() > 1, sd(stake_percent_q1) / sqrt(n()), 0),
            .groups = "drop") %>%
  filter(n >= 1)

ggplot(pair_stats, aes(x = reorder(stage3_q1_pair_id, mean_stake), y = mean_stake)) +
  geom_bar(stat = "identity", fill = PENN_BLUE, width = 0.7) +
  geom_errorbar(aes(ymin = pmax(0, mean_stake - se),
                    ymax = pmin(100, mean_stake + se)), width = 0.2) +
  geom_text(aes(label = sprintf("%.0f (n=%d)", mean_stake, n)),
            hjust = -0.1, size = 3.5) +
  scale_y_continuous(limits = c(0, 110), breaks = seq(0, 100, 20)) +
  coord_flip() +
  labs(title = "Mean Q1 Stake by Candidate Pair", x = NULL, y = "Mean Stake (%)") +
  theme_bw()
```

## 10.3 Response Time Analysis

```{r rt-analysis}
df_rt <- df %>% filter(rt_ms_stage3_q1 > 0)

if (nrow(df_rt) > 0) {
  df_rt <- df_rt %>%
    mutate(rt_sec_q1 = rt_ms_stage3_q1 / 1000,
           rt_sec_q2 = rt_ms_stage3_q2 / 1000)

  cat("Response time stats (seconds):\n")
  cat("  Q1: M =", round(mean(df_rt$rt_sec_q1, na.rm = TRUE), 1),
      "| Median =", round(median(df_rt$rt_sec_q1, na.rm = TRUE), 1),
      "| SD =", round(sd(df_rt$rt_sec_q1, na.rm = TRUE), 1), "\n")
  if (sum(df_rt$rt_sec_q2 > 0, na.rm = TRUE) > 0) {
    cat("  Q2: M =", round(mean(df_rt$rt_sec_q2[df_rt$rt_sec_q2 > 0], na.rm = TRUE), 1),
        "| Median =", round(median(df_rt$rt_sec_q2[df_rt$rt_sec_q2 > 0], na.rm = TRUE), 1), "\n")
  }

  ggplot(df_rt, aes(x = rt_sec_q1, y = stake_percent_q1, color = endorser_gender_f)) +
    geom_point(alpha = 0.6, size = 3) +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.15) +
    scale_color_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
    scale_x_continuous(trans = "log10") +
    scale_y_continuous(limits = c(0, 100)) +
    labs(title = "Q1 Stake vs. Response Time",
         subtitle = "Slower decisions may reflect more deliberation",
         x = "Q1 Response Time (seconds, log scale)", y = "Q1 Stake (%)",
         color = "Endorser Gender") +
    theme_bw() + theme(legend.position = "bottom")
} else {
  cat("No response time data available.\n")
}
```

\newpage

# 11. Preliminary Effect Sizes & Power

```{r effect-sizes}
man_stakes  <- df$stake_percent_q1[df$endorser_gender_code == "Man"]
woman_stakes <- df$stake_percent_q1[df$endorser_gender_code == "Woman"]

pooled_sd <- sqrt(((length(man_stakes) - 1) * var(man_stakes) +
                    (length(woman_stakes) - 1) * var(woman_stakes)) /
                   (length(man_stakes) + length(woman_stakes) - 2))
cohens_d <- (mean(man_stakes) - mean(woman_stakes)) / pooled_sd

cat("=== Preliminary Effect Sizes (Q1 Stake) ===\n\n")
cat("Gender effect:\n")
cat("  Man mean:", round(mean(man_stakes), 1), "(n=", length(man_stakes), ")\n")
cat("  Woman mean:", round(mean(woman_stakes), 1), "(n=", length(woman_stakes), ")\n")
cat("  Cohen's d:", round(cohens_d, 3), "\n\n")

r2 <- summary(model_rq3)$r.squared
cat("RQ3 model R-squared:", round(r2, 3), "\n")
cat("RQ3 model Adj. R-squared:", round(summary(model_rq3)$adj.r.squared, 3), "\n\n")

if (nrow(df_tc) >= 10 && exists("model_rq1")) {
  cat("=== Preliminary Effect Sizes (Trust Change) ===\n\n")
  cat("RQ1 model R-squared:", round(summary(model_rq1)$r.squared, 3), "\n")
  cat("RQ1 model Adj. R-squared:", round(summary(model_rq1)$adj.r.squared, 3), "\n")
}

cat("\n=== Power Note ===\n")
cat("Current N =", nrow(df), "(Q1) /", nrow(df_tc), "(trust change)\n")
cat("Target main study N = 600 evaluators\n")
cat("At current N, detectable effects are very large (d > ~0.8).\n")
cat("Primary value: verify mechanics, check data quality, observe directional patterns.\n")
```

\newpage

# 12. Summary

## Sample & Data Quality

```{r summary-table}
summary_tbl <- data.frame(
  Metric = c(
    "Total Prolific completions",
    "Passed comprehension check (Q42)",
    "Final analytic sample (all filters)",
    "With Q2 stake (trust change available)",
    "With response times",
    "Conditions covered (of 8)",
    "Median completion time"
  ),
  Value = c(
    nrow(d3),
    nrow(d4),
    nrow(df),
    nrow(df_tc),
    n_rt,
    n_conds,
    paste0(round(median(df$duration_min, na.rm = TRUE), 1), " min")
  )
)
styled_kable(summary_tbl)
```

## Early Directional Patterns

```{r early-signals}
cat("These are DESCRIPTIVE pilot patterns — not confirmatory tests.\n\n")

cat("1. GENDER on Q1 stake: Man M =", round(mean(man_stakes), 1),
    "vs. Woman M =", round(mean(woman_stakes), 1),
    "(d =", round(cohens_d, 2), ")\n")

strong_stakes <- df$stake_percent_q1[df$endorser_strong == 1]
weak_stakes   <- df$stake_percent_q1[df$endorser_strong == 0]
if (length(weak_stakes) > 1 && length(strong_stakes) > 1) {
  cat("2. STRENGTH on Q1 stake: Strong M =", round(mean(strong_stakes), 1),
      "vs. Weak M =", round(mean(weak_stakes), 1), "\n")
}

if (nrow(df_tc) > 0) {
  cat("3. TRUST CHANGE overall: M =", round(mean(df_tc$trust_change), 1),
      "(SD =", round(sd(df_tc$trust_change), 1), ")\n")
}
```

---

*Analysis generated `r Sys.time()` | Stage 3 Pilot (Study `r TARGET_STUDY`) | Sponsorship Network*
