---
title: "Cross-Pilot Comparison"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document:
    toc: no
    fig_caption: true
    latex_engine: xelatex
header-includes:
  - \usepackage{booktabs}
  - \usepackage{float}
  - \floatplacement{figure}{H}
  - \floatplacement{table}{H}
  - \usepackage{geometry}
  - \geometry{margin=0.9in}
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.width = 10, fig.height = 5.5, fig.pos = "H"
)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)

NAVY <- "#011F5B"
RED  <- "#990000"
```

```{r load-data}
# ── Old pilots (shared raw export) ──
raw <- read.csv("../old/output/stage3_pilot_data.csv", stringsAsFactors = FALSE)
raw <- raw[-c(1, 2), ]
for (col in c("stake_percent_q1", "stake_percent_q2",
              "endorser_slider_value_q1", "endorser_slider_value_q2",
              "Finished", "stage3_q1_is_correct")) {
  if (col %in% names(raw)) raw[[col]] <- suppressWarnings(as.numeric(raw[[col]]))
}

prep_old <- function(df) {
  df <- df %>%
    filter(Q42 == "2",
           !is.na(assigned_condition), trimws(assigned_condition) != "",
           !is.na(stake_percent_q1)) %>%
    mutate(
      gender   = ifelse(grepl("^M_", assigned_condition), "Male", "Female"),
      outcome  = ifelse(stage3_q1_is_correct == 1, "Success", "Failure"),
      strength = ifelse(grepl("_strong$", assigned_condition), "Strong", "Weak"),
      trust_change = stake_percent_q2 - stake_percent_q1,
      trust_d1 = stake_percent_q1,
      q44_resp = case_when(Q44 == "1" ~ "Male", Q44 == "2" ~ "Female", TRUE ~ NA_character_),
      manip_pass = (q44_resp == gender)
    ) %>%
    filter(!is.na(trust_change))
  df$gender   <- factor(df$gender,   levels = c("Male", "Female"))
  df$outcome  <- factor(df$outcome,  levels = c("Failure", "Success"))
  df$strength <- factor(df$strength, levels = c("Weak", "Strong"))
  df
}

base <- raw %>%
  filter(Status != "1", Finished == 1,
         !is.na(PROLIFIC_PID), trimws(PROLIFIC_PID) != "")

d100_full <- prep_old(base %>% filter(STUDY_ID == "698e27db580428e78f8e9ff1"))
d400_full <- prep_old(base %>% filter(STUDY_ID == "699503492f16351efc6be595"))

d100 <- d100_full %>% filter(manip_pass == TRUE)
d400 <- d400_full %>% filter(manip_pass == TRUE)

# ── Latest pilot (best quality) ──
latest <- read.csv("study_data_clean.csv", stringsAsFactors = FALSE) %>%
  filter(best_participant == 1) %>%
  mutate(
    gender   = factor(endorser_gender, levels = c("Male", "Female")),
    outcome  = factor(outcome, levels = c("Failure", "Success")),
    strength = factor(ifelse(strength_cond == "strong", "Strong", "Weak"),
                      levels = c("Weak", "Strong"))
  )

pilots <- list(
  list(data = d100,   label = sprintf("Pilot 1 (N = %d)", nrow(d100)),   short = "Pilot 1"),
  list(data = d400,   label = sprintf("Pilot 2 (N = %d)", nrow(d400)),   short = "Pilot 2"),
  list(data = latest, label = sprintf("Pilot 3 — Best Quality (N = %d)", nrow(latest)), short = "Pilot 3 (Best)")
)
```

All three samples are restricted to participants who correctly identified the sponsor's gender (manipulation check pass). Pilot 3 additionally requires all 4 comprehension checks correct.

- **Pilot 1**: N = `r nrow(d100)` after manip-check filter (from `r nrow(d100_full)` total)
- **Pilot 2**: N = `r nrow(d400)` after manip-check filter (from `r nrow(d400_full)` total)
- **Pilot 3**: N = `r nrow(latest)` (CQ perfect + manip pass, from `r nrow(read.csv("study_data_clean.csv"))` total)

# RQ1: Gender $\times$ Outcome

```{r rq1-combined-fig, fig.height=4.5, fig.width=11, fig.cap="Trust Change by Sponsor Gender and Outcome across pilots. Error bars = +/- 1 SE."}
all_rq1 <- bind_rows(
  lapply(pilots, function(p) {
    p$data %>%
      group_by(gender, outcome) %>%
      summarise(m = mean(trust_change), se = sd(trust_change) / sqrt(n()),
                n = n(), .groups = "drop") %>%
      mutate(pilot = p$short)
  })
) %>%
  mutate(pilot = factor(pilot, levels = sapply(pilots, `[[`, "short")))

ggplot(all_rq1, aes(x = outcome, y = m, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = m - se, ymax = m + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", m, n),
                vjust = ifelse(m >= 0, -0.5, 1.5)),
            position = position_dodge(0.8),
            size = 3, fontface = "bold") +
  facet_wrap(~ pilot, nrow = 1) +
  scale_fill_manual(values = c("Male" = NAVY, "Female" = RED)) +
  scale_y_continuous(limits = c(-20, 30), breaks = seq(-20, 30, 10)) +
  labs(x = "Decision 1 Outcome", y = "Mean Trust Change (D2 - D1)",
       fill = "Sponsor Gender") +
  theme_bw() +
  theme(legend.position = "bottom",
        strip.text = element_text(size = 12, face = "bold"),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12))
```

```{r rq1-summary-table}
rq1_summary <- bind_rows(lapply(pilots, function(p) {
  m <- lm(trust_change ~ gender * outcome, data = p$data)
  cs <- summary(m)$coefficients
  ix <- "genderFemale:outcomeSuccess"
  male_b <- cs["outcomeSuccess", "Estimate"]
  female_b <- male_b + cs[ix, "Estimate"]
  tibble(
    Pilot = p$short,
    N = nrow(p$data),
    `Male Success Boost` = round(male_b, 1),
    `Female Success Boost` = round(female_b, 1),
    `Interaction b` = round(cs[ix, "Estimate"], 1),
    `Interaction p` = round(cs[ix, "Pr(>|t|)"], 3)
  )
}))

kable(rq1_summary, booktabs = TRUE, row.names = FALSE,
      caption = "Gender x Outcome interaction on trust change")
```

\newpage

# Three-Way Interaction: Gender $\times$ Strength $\times$ Outcome

```{r rq4-combined-fig, fig.height=6.5, fig.width=11, fig.cap="Trust Change by Sponsor Gender, Strength, and Outcome across pilots. Error bars = +/- 1 SE."}
all_rq4 <- bind_rows(
  lapply(pilots, function(p) {
    p$data %>%
      group_by(gender, strength, outcome) %>%
      summarise(m = mean(trust_change), se = sd(trust_change) / sqrt(n()),
                n = n(), .groups = "drop") %>%
      mutate(pilot = p$short)
  })
) %>%
  mutate(pilot = factor(pilot, levels = sapply(pilots, `[[`, "short")))

ggplot(all_rq4, aes(x = outcome, y = m, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = m - se, ymax = m + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", m, n),
                vjust = ifelse(m >= 0, -0.3, 1.3)),
            position = position_dodge(0.8),
            size = 2.5, fontface = "bold") +
  facet_grid(strength ~ pilot,
             labeller = labeller(
               strength = c("Weak" = "Weak Endorsement", "Strong" = "Strong Endorsement"))) +
  scale_fill_manual(values = c("Male" = NAVY, "Female" = RED)) +
  scale_y_continuous(breaks = seq(-40, 50, 10)) +
  labs(x = "Decision 1 Outcome", y = "Mean Trust Change (D2 - D1)",
       fill = "Sponsor Gender") +
  theme_bw() +
  theme(legend.position = "bottom",
        strip.text = element_text(size = 11, face = "bold"),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12))
```

```{r rq4-regression-summary}
rq4_summary <- bind_rows(lapply(pilots, function(p) {
  m <- lm(trust_change ~ gender * strength * outcome, data = p$data)
  cs <- summary(m)$coefficients

  go  <- "genderFemale:outcomeSuccess"
  gso <- "genderFemale:strengthStrong:outcomeSuccess"

  safe_b <- function(term) if (term %in% rownames(cs)) round(cs[term, "Estimate"], 1) else NA
  safe_p <- function(term) if (term %in% rownames(cs)) round(cs[term, "Pr(>|t|)"], 3) else NA

  tibble(
    Pilot = p$short,
    N = nrow(p$data),
    `Gender x Outcome b` = safe_b(go),
    `Gender x Outcome p` = safe_p(go),
    `3-Way b` = safe_b(gso),
    `3-Way p` = safe_p(gso)
  )
}))

kable(rq4_summary, booktabs = TRUE, row.names = FALSE,
      caption = "Three-way interaction regression summary")
```
