---
title: "Sponsorship Network — Stage 3 Pilot Analysis"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    fig_caption: true
    latex_engine: xelatex
header-includes:
  - \usepackage{booktabs}
  - \usepackage{float}
  - \floatplacement{figure}{H}
  - \floatplacement{table}{H}
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.width = 10, fig.height = 5.5, fig.pos = "H"
)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(car)
library(broom)
library(gridExtra)

NAVY <- "#011F5B"
RED  <- "#990000"
set.seed(42)
```

```{r load-data}
d <- read.csv("study_data_clean.csv", stringsAsFactors = FALSE) %>%
  mutate(
    endorser_gender_f = factor(endorser_gender, levels = c("Male", "Female")),
    outcome_f = factor(outcome, levels = c("Failure", "Success")),
    strength_f = factor(strength_cond, levels = c("weak", "strong")),
    trust_change = as.numeric(trust_change)
  )

# Three subsamples
s1 <- d                                          # Full
s2 <- d %>% filter(cq_score == 4)                # CQ = 4
s3 <- d %>% filter(best_participant == 1)         # CQ = 4 + Manip pass

samples <- list(
  list(data = s1, label = sprintf("Full Sample (N = %d)", nrow(s1))),
  list(data = s2, label = sprintf("CQ = 4 (N = %d)", nrow(s2))),
  list(data = s3, label = sprintf("CQ = 4 + Manip Pass (N = %d)", nrow(s3)))
)
```

\newpage

# Sample Overview

```{r sample-overview}
tibble(
  Sample = c("Full", "CQ = 4", "CQ = 4 + Manip Pass"),
  N = c(nrow(s1), nrow(s2), nrow(s3)),
  `Mean D1` = c(mean(s1$trust_d1), mean(s2$trust_d1), mean(s3$trust_d1)),
  `Mean D2` = c(mean(s1$trust_d2), mean(s2$trust_d2), mean(s3$trust_d2)),
  `Mean Change` = c(mean(s1$trust_change), mean(s2$trust_change), mean(s3$trust_change)),
  `SD Change` = c(sd(s1$trust_change), sd(s2$trust_change), sd(s3$trust_change)),
  `No Change %` = c(mean(s1$trust_change == 0), mean(s2$trust_change == 0),
                     mean(s3$trust_change == 0)) * 100
) %>%
  kable(digits = 1, caption = "DV descriptives by sample", booktabs = TRUE)
```

```{r dv-distribution, fig.height=8, fig.width=11, fig.cap="Distribution of Trust Change by Strength x Outcome"}
library(patchwork)

hist_facet <- function(dat, label) {
  # Compute cell means for vertical lines
  cell_means <- dat %>%
    group_by(strength_f, outcome_f) %>%
    summarise(m = mean(trust_change), n = n(), .groups = "drop")

  ggplot(dat, aes(x = trust_change)) +
    geom_histogram(binwidth = 5, fill = NAVY, color = "white", alpha = 0.8) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
    geom_vline(data = cell_means, aes(xintercept = m),
               linetype = "solid", color = RED, linewidth = 0.8) +
    geom_text(data = cell_means, aes(x = m, y = Inf,
              label = sprintf("M=%.1f (n=%d)", m, n)),
              vjust = 1.5, hjust = -0.05, color = RED, fontface = "bold", size = 3) +
    facet_grid(strength_f ~ outcome_f,
               labeller = labeller(
                 strength_f = c("weak" = "Weak Endorser", "strong" = "Strong Endorser"),
                 outcome_f = c("Failure" = "Failure", "Success" = "Success"))) +
    labs(title = label, x = "Trust Change (D2 - D1)", y = "Count") +
    theme_bw() +
    theme(plot.title = element_text(size = 12, face = "bold"),
          strip.text = element_text(size = 11, face = "bold"))
}

hist_facet(s1, sprintf("Full Sample (N = %d)", nrow(s1)))
```

```{r dv-distribution-cq4, fig.height=8, fig.width=11, fig.cap="Distribution of Trust Change by Strength x Outcome (CQ = 4)"}
hist_facet(s2, sprintf("CQ = 4 (N = %d)", nrow(s2)))
```

```{r dv-distribution-best, fig.height=8, fig.width=11, fig.cap="Distribution of Trust Change by Strength x Outcome (CQ = 4 + Manip Pass)"}
hist_facet(s3, sprintf("CQ = 4 + Manip Pass (N = %d)", nrow(s3)))
```

\newpage

# RQ1: Gender $\times$ Outcome on Trust Change

Does endorser gender moderate how evaluators respond to outcome feedback?

$$\text{TrustChange}_i = \beta_0 + \beta_1\text{Female} + \beta_2\text{Success} + \beta_3(\text{Female} \times \text{Success}) + \varepsilon_i$$

## Full Sample (N = `r nrow(s1)`)

```{r rq1-fig-full, fig.height=5, fig.cap="RQ1: Full Sample"}
plot_rq1 <- function(dat, title_label) {
  pd <- dat %>%
    group_by(endorser_gender_f, outcome_f) %>%
    summarise(m = mean(trust_change), se = sd(trust_change) / sqrt(n()),
              n = n(), .groups = "drop") %>%
    mutate(
      ci_hi = m + 1.96 * se,
      ci_lo = m - 1.96 * se,
      label_y = ifelse(m >= 0, ci_hi + 1, ci_lo - 1),
      label_vjust = ifelse(m >= 0, 0, 1)
    )

  y_max <- max(pd$ci_hi) + 10
  y_min <- min(pd$ci_lo) - 10

  ggplot(pd, aes(x = outcome_f, y = m, fill = endorser_gender_f)) +
    geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
    geom_errorbar(aes(ymin = ci_lo, ymax = ci_hi),
                  position = position_dodge(0.8), width = 0.25) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    geom_text(aes(y = label_y, label = sprintf("%.1f (n=%d)", m, n),
                  vjust = label_vjust),
              position = position_dodge(0.8),
              size = 3.5, fontface = "bold") +
    scale_fill_manual(values = c("Male" = NAVY, "Female" = RED)) +
    coord_cartesian(ylim = c(y_min, y_max)) +
    labs(title = title_label, x = "D1 Outcome",
         y = "Trust Change (D2 - D1)", fill = "Endorser Gender") +
    theme_bw() +
    theme(legend.position = "bottom",
          plot.title = element_text(size = 14, face = "bold"),
          axis.text = element_text(size = 12),
          axis.title = element_text(size = 13))
}

plot_rq1(s1, sprintf("RQ1: Gender x Outcome — Full Sample (N = %d)", nrow(s1)))
```

```{r rq1-reg-full, results='markup'}
summary(lm(trust_change ~ endorser_gender_f * outcome_f, data = s1))
```

\newpage

## CQ = 4 (N = `r nrow(s2)`)

```{r rq1-fig-cq4, fig.height=5, fig.cap="RQ1: CQ = 4"}
plot_rq1(s2, sprintf("RQ1: Gender x Outcome — CQ = 4 (N = %d)", nrow(s2)))
```

```{r rq1-reg-cq4, results='markup'}
summary(lm(trust_change ~ endorser_gender_f * outcome_f, data = s2))
```

\newpage

## CQ = 4 + Manip Pass (N = `r nrow(s3)`)

```{r rq1-fig-best, fig.height=5, fig.cap="RQ1: CQ = 4 + Manip Pass"}
plot_rq1(s3, sprintf("RQ1: Gender x Outcome — CQ = 4 + Manip Pass (N = %d)", nrow(s3)))
```

```{r rq1-reg-best, results='markup'}
summary(lm(trust_change ~ endorser_gender_f * outcome_f, data = s3))
```

\newpage

## RQ1 Summary

```{r rq1-summary}
rq1_row <- function(dat, label) {
  m <- lm(trust_change ~ endorser_gender_f * outcome_f, data = dat)
  cs <- summary(m)$coefficients
  ix_row <- "endorser_gender_fFemale:outcome_fSuccess"
  # Cell means
  mf <- mean(dat$trust_change[dat$endorser_gender == "Male" & dat$outcome == "Failure"])
  ms <- mean(dat$trust_change[dat$endorser_gender == "Male" & dat$outcome == "Success"])
  ff <- mean(dat$trust_change[dat$endorser_gender == "Female" & dat$outcome == "Failure"])
  fs <- mean(dat$trust_change[dat$endorser_gender == "Female" & dat$outcome == "Success"])
  tibble(
    Sample = label, N = nrow(dat),
    `Male Fail` = mf, `Male Suc` = ms, `Male Range` = ms - mf,
    `Fem Fail` = ff, `Fem Suc` = fs, `Fem Range` = fs - ff,
    `Interaction b` = cs[ix_row, "Estimate"],
    `p` = cs[ix_row, "Pr(>|t|)"],
    `d` = cs[ix_row, "Estimate"] / sd(dat$trust_change)
  )
}

bind_rows(
  rq1_row(s1, "Full"),
  rq1_row(s2, "CQ = 4"),
  rq1_row(s3, "CQ=4 + Manip")
) %>%
  kable(digits = c(0, 0, 1, 1, 1, 1, 1, 1, 2, 3, 3),
        caption = "RQ1: Gender x Outcome across samples", booktabs = TRUE)
```

\newpage

# RQ2: Gender $\times$ Strength $\times$ Outcome on Trust Change

Does endorser confidence moderate the gender effect on trust updating?

$$\text{TrustChange}_i = \beta_0 + \beta_1 F + \beta_2 S + \beta_3 O + \beta_4(F \times S) + \beta_5(F \times O) + \beta_6(S \times O) + \beta_7(F \times S \times O) + \varepsilon_i$$

## Full Sample (N = `r nrow(s1)`)

```{r rq2-fig-full, fig.height=5, fig.width=12, fig.cap="RQ2: Full Sample"}
plot_rq2 <- function(dat, title_label) {
  pd <- dat %>%
    group_by(endorser_gender_f, outcome_f, strength_f) %>%
    summarise(m = mean(trust_change), se = sd(trust_change) / sqrt(n()),
              n = n(), .groups = "drop") %>%
    mutate(
      ci_hi = m + 1.96 * se,
      ci_lo = m - 1.96 * se,
      label_y = ifelse(m >= 0, ci_hi + 1, ci_lo - 1),
      label_vjust = ifelse(m >= 0, 0, 1)
    )

  y_max <- max(pd$ci_hi) + 8
  y_min <- min(pd$ci_lo) - 8

  ggplot(pd, aes(x = outcome_f, y = m, fill = endorser_gender_f)) +
    geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
    geom_errorbar(aes(ymin = ci_lo, ymax = ci_hi),
                  position = position_dodge(0.8), width = 0.25) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    geom_text(aes(y = label_y, label = sprintf("%.1f (n=%d)", m, n),
                  vjust = label_vjust),
              position = position_dodge(0.8),
              size = 3, fontface = "bold") +
    facet_wrap(~ strength_f, nrow = 1,
               labeller = labeller(strength_f = c("weak" = "Weak Endorser",
                                                   "strong" = "Strong Endorser"))) +
    scale_fill_manual(values = c("Male" = NAVY, "Female" = RED)) +
    coord_cartesian(ylim = c(y_min, y_max)) +
    labs(title = title_label, x = "D1 Outcome",
         y = "Trust Change (D2 - D1)", fill = "Endorser Gender") +
    theme_bw() +
    theme(legend.position = "bottom",
          plot.title = element_text(size = 14, face = "bold"),
          strip.text = element_text(size = 13, face = "bold"),
          axis.text = element_text(size = 11),
          axis.title = element_text(size = 13))
}

plot_rq2(s1, sprintf("RQ2: Gender x Strength x Outcome — Full Sample (N = %d)", nrow(s1)))
```

```{r rq2-reg-full, results='markup'}
summary(lm(trust_change ~ endorser_gender_f * strength_f * outcome_f, data = s1))
```

\newpage

## CQ = 4 (N = `r nrow(s2)`)

```{r rq2-fig-cq4, fig.height=5, fig.width=12, fig.cap="RQ2: CQ = 4"}
plot_rq2(s2, sprintf("RQ2: Gender x Strength x Outcome — CQ = 4 (N = %d)", nrow(s2)))
```

```{r rq2-reg-cq4, results='markup'}
summary(lm(trust_change ~ endorser_gender_f * strength_f * outcome_f, data = s2))
```

\newpage

## CQ = 4 + Manip Pass (N = `r nrow(s3)`)

```{r rq2-fig-best, fig.height=5, fig.width=12, fig.cap="RQ2: CQ = 4 + Manip Pass"}
plot_rq2(s3, sprintf("RQ2: Gender x Strength x Outcome — CQ = 4 + Manip Pass (N = %d)", nrow(s3)))
```

```{r rq2-reg-best, results='markup'}
summary(lm(trust_change ~ endorser_gender_f * strength_f * outcome_f, data = s3))
```

\newpage

## RQ2 Summary: Outcome Range by Gender $\times$ Strength

```{r rq2-summary}
rq2_row <- function(dat, label) {
  cells <- dat %>%
    group_by(endorser_gender_f, strength_f, outcome_f) %>%
    summarise(m = mean(trust_change), n = n(), .groups = "drop") %>%
    pivot_wider(names_from = outcome_f, values_from = c(m, n))

  cells %>%
    mutate(
      Sample = label,
      Range = m_Success - m_Failure
    ) %>%
    select(Sample, Gender = endorser_gender_f, Strength = strength_f,
           Failure = m_Failure, `n Fail` = n_Failure,
           Success = m_Success, `n Suc` = n_Success,
           Range)
}

bind_rows(
  rq2_row(s1, "Full"),
  rq2_row(s2, "CQ = 4"),
  rq2_row(s3, "CQ=4+Manip")
) %>%
  kable(digits = 1,
        caption = "RQ2: Outcome range (Success - Failure) by Gender x Strength across samples",
        booktabs = TRUE)
```

```{r rq2-interaction-summary}
rq2_ix <- function(dat, label) {
  m <- lm(trust_change ~ endorser_gender_f * strength_f * outcome_f, data = dat)
  cs <- summary(m)$coefficients
  gs_row <- "endorser_gender_fFemale:strength_fstrong"
  three_row <- "endorser_gender_fFemale:strength_fstrong:outcome_fSuccess"
  tibble(
    Sample = label, N = nrow(dat),
    `Gender x Strength b` = cs[gs_row, "Estimate"],
    `G x S p` = cs[gs_row, "Pr(>|t|)"],
    `3-Way b` = cs[three_row, "Estimate"],
    `3-Way p` = cs[three_row, "Pr(>|t|)"]
  )
}

bind_rows(
  rq2_ix(s1, "Full"),
  rq2_ix(s2, "CQ = 4"),
  rq2_ix(s3, "CQ=4 + Manip")
) %>%
  kable(digits = c(0, 0, 2, 3, 2, 3),
        caption = "RQ2: Key interaction coefficients across samples", booktabs = TRUE)
```

\newpage

# RQ3: Initial Trust by Gender $\times$ Strength

Do evaluators extend different levels of initial trust to male versus female endorsers, and does endorsement strength moderate this?

$$\text{D1 Wager}_i = \beta_0 + \beta_1\text{Female} + \beta_2\text{Strong} + \beta_3(\text{Female} \times \text{Strong}) + \varepsilon_i$$

## Full Sample (N = `r nrow(s1)`)

```{r rq3-fig-full, fig.height=5, fig.cap="RQ3: Full Sample"}
plot_rq3 <- function(dat, title_label) {
  pd <- dat %>%
    group_by(endorser_gender_f, strength_f) %>%
    summarise(m = mean(trust_d1), se = sd(trust_d1) / sqrt(n()),
              n = n(), .groups = "drop") %>%
    mutate(
      ci_hi = m + 1.96 * se,
      ci_lo = m - 1.96 * se
    )

  y_max <- max(pd$ci_hi) + 10

  ggplot(pd, aes(x = strength_f, y = m, fill = endorser_gender_f)) +
    geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
    geom_errorbar(aes(ymin = ci_lo, ymax = ci_hi),
                  position = position_dodge(0.8), width = 0.25) +
    geom_text(aes(y = ci_hi + 1, label = sprintf("%.1f (n=%d)", m, n)),
              position = position_dodge(0.8),
              vjust = 0,
              size = 3.5, fontface = "bold") +
    scale_fill_manual(values = c("Male" = NAVY, "Female" = RED)) +
    scale_x_discrete(labels = c("weak" = "Weak Endorser", "strong" = "Strong Endorser")) +
    coord_cartesian(ylim = c(0, y_max)) +
    labs(title = title_label, x = "Endorsement Strength",
         y = "Initial Wager (D1)", fill = "Endorser Gender") +
    theme_bw() +
    theme(legend.position = "bottom",
          plot.title = element_text(size = 14, face = "bold"),
          axis.text = element_text(size = 12),
          axis.title = element_text(size = 13))
}

plot_rq3(s1, sprintf("RQ3: Initial Trust by Gender x Strength — Full Sample (N = %d)", nrow(s1)))
```

```{r rq3-reg-full, results='markup'}
summary(lm(trust_d1 ~ endorser_gender_f * strength_f, data = s1))
```

\newpage

## CQ = 4 (N = `r nrow(s2)`)

```{r rq3-fig-cq4, fig.height=5, fig.cap="RQ3: CQ = 4"}
plot_rq3(s2, sprintf("RQ3: Initial Trust by Gender x Strength — CQ = 4 (N = %d)", nrow(s2)))
```

```{r rq3-reg-cq4, results='markup'}
summary(lm(trust_d1 ~ endorser_gender_f * strength_f, data = s2))
```

\newpage

## CQ = 4 + Manip Pass (N = `r nrow(s3)`)

```{r rq3-fig-best, fig.height=5, fig.cap="RQ3: CQ = 4 + Manip Pass"}
plot_rq3(s3, sprintf("RQ3: Initial Trust by Gender x Strength — CQ = 4 + Manip Pass (N = %d)", nrow(s3)))
```

```{r rq3-reg-best, results='markup'}
summary(lm(trust_d1 ~ endorser_gender_f * strength_f, data = s3))
```

\newpage

## RQ3 Summary

```{r rq3-summary}
rq3_row <- function(dat, label) {
  mw_w <- mean(dat$trust_d1[dat$endorser_gender == "Male" & dat$strength_cond == "weak"])
  ms_w <- mean(dat$trust_d1[dat$endorser_gender == "Male" & dat$strength_cond == "strong"])
  fw_w <- mean(dat$trust_d1[dat$endorser_gender == "Female" & dat$strength_cond == "weak"])
  fs_w <- mean(dat$trust_d1[dat$endorser_gender == "Female" & dat$strength_cond == "strong"])

  m <- lm(trust_d1 ~ endorser_gender_f * strength_f, data = dat)
  cs <- summary(m)$coefficients
  fem_row <- "endorser_gender_fFemale"
  ix_row <- "endorser_gender_fFemale:strength_fstrong"

  tibble(
    Sample = label, N = nrow(dat),
    `M Weak` = mw_w, `M Strong` = ms_w, `M Diff` = ms_w - mw_w,
    `F Weak` = fw_w, `F Strong` = fs_w, `F Diff` = fs_w - fw_w,
    `Female b` = cs[fem_row, "Estimate"],
    `Female p` = cs[fem_row, "Pr(>|t|)"],
    `G x S b` = cs[ix_row, "Estimate"],
    `G x S p` = cs[ix_row, "Pr(>|t|)"]
  )
}

bind_rows(
  rq3_row(s1, "Full"),
  rq3_row(s2, "CQ = 4"),
  rq3_row(s3, "CQ=4 + Manip")
) %>%
  kable(digits = c(0, 0, 1, 1, 1, 1, 1, 1, 2, 3, 2, 3),
        caption = "RQ3: Initial trust (D1 wager) by Gender x Strength across samples",
        booktabs = TRUE)
```