---
title: "Sponsorship Network — Pilot Analysis (Real Data)"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document:
    toc: no
    fig_caption: true
    latex_engine: xelatex
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6
)
library(dplyr)
library(ggplot2)
library(broom)
library(knitr)
library(tidyverse)

set.seed(42)
```

```{r load-data}
d <- read.csv("pilot_data_clean.csv", stringsAsFactors = FALSE) %>%
  mutate(
    endorser_gender_f = factor(endorser_gender, levels = c("Male", "Female")),
    outcome_f = factor(outcome, levels = c("Failure", "Success")),
    strength_cond_f = factor(strength_condition, levels = c("weak", "strong")),
    # Center abs_strength for interactions
    abs_strength_c = abs_strength - mean(abs_strength, na.rm = TRUE),
    # Binary female indicator for coefficient interpretation
    female = ifelse(endorser_gender == "Female", 1, 0),
    success = ifelse(outcome == "Success", 1, 0)
  )

n_total <- nrow(d)
n_male <- sum(d$endorser_gender == "Male")
n_female <- sum(d$endorser_gender == "Female")
```

# Overview

**N = `r n_total`** evaluators (`r n_male` Male endorser, `r n_female` Female endorser) from Prolific pilot.

Each evaluator sees ONE endorser making TWO decisions:

1. **Decision 1**: See endorsement + strength → wager trust → learn outcome
2. **Decision 2**: Same endorser, new candidate → wager trust again
3. **Trust Change = D2 - D1** (primary DV)

## Sample Description

```{r sample-table}
d %>%
  group_by(endorser_gender_f, outcome_f, strength_cond_f) %>%
  summarise(
    n = n(),
    mean_d1 = mean(trust_d1),
    mean_d2 = mean(trust_d2),
    mean_change = mean(trust_change),
    sd_change = sd(trust_change),
    .groups = "drop"
  ) %>%
  kable(digits = 1, col.names = c("Gender", "Outcome", "Strength", "N",
                                    "Mean D1", "Mean D2", "Mean Change", "SD Change"),
        caption = "Cell means by condition")
```

\newpage

# RQ1: Trust Change by Sponsor Gender × Outcome

**Hypothesis (HQ1)**: Female sponsors are punished **more** for failures and rewarded **less** for successes.

$$
\text{TrustChange}_{i} = \beta_0 + \beta_1 \text{Female}_{i} + \beta_2 \text{Success}_{i}
+ \beta_3 (\text{Female}_{i} \times \text{Success}_{i}) + \epsilon_{i}
$$

```{r rq1-model, results='markup'}
model_rq1 <- lm(trust_change ~ endorser_gender_f * outcome_f, data = d)
summary(model_rq1)
```

\newpage

## Visualization

```{r rq1-fig, fig.height=5, fig.cap="RQ1: Trust Change by Sponsor Gender and Outcome"}
plot_rq1 <- d %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(
    mean_change = mean(trust_change),
    se = sd(trust_change) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(plot_rq1,
       aes(x = outcome_f, y = mean_change, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_change - 1.96 * se, ymax = mean_change + 1.96 * se),
                position = position_dodge(0.8), width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_change, n)),
            position = position_dodge(0.8),
            vjust = ifelse(plot_rq1$mean_change > 0, -0.3, 1.3),
            size = 4, fontface = "bold") +
  scale_fill_manual(values = c("Male" = "#011F5B", "Female" = "#990000")) +
  labs(
    title = "RQ1: Are Female Sponsors Punished More and Rewarded Less?",
    subtitle = "Trust Change (D2 - D1) by Sponsor Gender and D1 Outcome",
    x = "Decision 1 Outcome",
    y = "Trust Change (%)",
    fill = "Endorser Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 13)
  )
```

\newpage

# RQ3: Initial Trust by Sponsor Gender × Endorsement Strength

**Hypothesis (HQ3)**: Female sponsors need **higher** endorsement strength to achieve same initial trust.

$$
\text{InitialTrust}_{i} = \beta_0 + \beta_1 \text{Female}_{i} + \beta_2 \text{AbsStrength}_{i}
+ \beta_3 (\text{Female}_{i} \times \text{AbsStrength}_{i}) + \epsilon_{i}
$$

```{r rq3-model, results='markup'}
model_rq3 <- lm(trust_d1 ~ endorser_gender_f * abs_strength, data = d)
summary(model_rq3)
```

\newpage

## Visualization

```{r rq3-fig, fig.height=6, fig.cap="RQ3: Initial Trust by Sponsor Gender and Endorsement Strength"}
ggplot(d, aes(x = abs_strength, y = trust_d1,
              color = endorser_gender_f, fill = endorser_gender_f)) +
  geom_point(alpha = 0.3, size = 1.5) +
  geom_smooth(method = "lm", se = TRUE, alpha = 0.15) +
  scale_color_manual(values = c("Male" = "#011F5B", "Female" = "#990000")) +
  scale_fill_manual(values = c("Male" = "#011F5B", "Female" = "#990000")) +
  scale_x_continuous(breaks = seq(0, 100, 10)) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "RQ3: Do Female Sponsors Need Higher Strength for Same Trust?",
    subtitle = "Initial Trust (D1) by Endorsement Strength",
    x = "Endorsement Strength (|slider - 50| × 2)",
    y = "Initial Trust (Wager %)",
    color = "Endorser Gender",
    fill = "Endorser Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13)
  )
```

\newpage

# RQ4: Trust Change by Gender × Strength × Outcome (3-Way)

**Hypothesis (HQ4)**: Trust change is **more** contingent on strength × outcome for female sponsors.

$$
\text{TrustChange}_{i} = \beta_0 + \beta_1 \text{Female} + \beta_2 \text{Strength}^c + \beta_3 \text{Success}
+ \beta_4 (\text{F} \times \text{Str}^c) + \beta_5 (\text{F} \times \text{Suc})
+ \beta_6 (\text{Str}^c \times \text{Suc}) + \beta_7 (\text{F} \times \text{Str}^c \times \text{Suc}) + \epsilon
$$

```{r rq4-model, results='markup'}
model_rq4 <- lm(trust_change ~ endorser_gender_f * abs_strength_c * outcome_f,
                data = d)
summary(model_rq4)
```

\newpage

## Visualization

```{r rq4-fig, fig.height=6, fig.width=11, fig.cap="RQ4: Trust Change by Sponsor Gender, Strength, and Outcome"}
ggplot(d, aes(x = abs_strength, y = trust_change,
              color = outcome_f, fill = outcome_f)) +
  geom_point(alpha = 0.2, size = 1) +
  geom_smooth(method = "lm", se = TRUE, alpha = 0.15) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  facet_wrap(~ endorser_gender_f, nrow = 1) +
  scale_color_manual(values = c("Failure" = "#C62828", "Success" = "#2E7D32"),
                     labels = c("Incorrect", "Correct")) +
  scale_fill_manual(values = c("Failure" = "#C62828", "Success" = "#2E7D32"),
                    labels = c("Incorrect", "Correct")) +
  scale_x_continuous(breaks = seq(0, 100, 20)) +
  labs(
    title = "RQ4: Is Trust Change More Sensitive to Strength × Outcome for Females?",
    x = "Endorsement Strength (|slider - 50| × 2)",
    y = "Trust Change (D2 - D1)",
    color = "D1 Outcome",
    fill = "D1 Outcome"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    strip.text = element_text(size = 13, face = "bold"),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13)
  )
```

\newpage

# RQ1 + RQ4 Combined: Bar Chart by Full Condition

```{r combined-fig, fig.height=6, fig.width=11, fig.cap="Trust Change by Full 2×2×2 Condition"}
plot_full <- d %>%
  group_by(endorser_gender_f, outcome_f, strength_cond_f) %>%
  summarise(
    mean_change = mean(trust_change),
    se = sd(trust_change) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(plot_full,
       aes(x = interaction(outcome_f, strength_cond_f, sep = "\n"),
           y = mean_change, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_change - 1.96 * se, ymax = mean_change + 1.96 * se),
                position = position_dodge(0.8), width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = sprintf("%.1f", mean_change)),
            position = position_dodge(0.8),
            vjust = ifelse(plot_full$mean_change > 0, -0.5, 1.5),
            size = 3.5, fontface = "bold") +
  scale_fill_manual(values = c("Male" = "#011F5B", "Female" = "#990000")) +
  labs(
    title = "Trust Change by Full 2×2×2 Design",
    subtitle = "Gender × Outcome × Endorsement Strength",
    x = "Outcome × Strength",
    y = "Trust Change (D2 - D1)",
    fill = "Endorser Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13)
  )
```

\newpage

# Summary Statistics

```{r summary-stats}
# Overall
cat("Overall Trust Change: mean =", round(mean(d$trust_change), 1),
    ", sd =", round(sd(d$trust_change), 1), "\n")
cat("Overall Trust D1: mean =", round(mean(d$trust_d1), 1),
    ", sd =", round(sd(d$trust_d1), 1), "\n")
cat("Overall Trust D2: mean =", round(mean(d$trust_d2), 1),
    ", sd =", round(sd(d$trust_d2), 1), "\n\n")

# By condition
d %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(
    n = n(),
    mean_d1 = round(mean(trust_d1), 1),
    mean_d2 = round(mean(trust_d2), 1),
    mean_change = round(mean(trust_change), 1),
    sd_change = round(sd(trust_change), 1),
    .groups = "drop"
  ) %>%
  kable(col.names = c("Gender", "Outcome", "N", "Mean D1", "Mean D2",
                        "Mean Change", "SD Change"),
        caption = "Summary by Gender × Outcome")
```

```{r duration-stats}
d %>%
  summarise(
    median_duration_s = median(as.numeric(duration_s), na.rm = TRUE),
    mean_duration_s = mean(as.numeric(duration_s), na.rm = TRUE),
    median_rt_d1 = median(as.numeric(rt_d1), na.rm = TRUE),
    median_rt_d2 = median(as.numeric(rt_d2), na.rm = TRUE)
  ) %>%
  kable(digits = 0, caption = "Timing statistics")
```
