---
title: "Sponsorship Simulations"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document:
    toc: no
    fig_caption: true
    latex_engine: xelatex
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.width = 10,
	fig.height = 6
)
library(dplyr)
library(ggplot2)
library(broom)
library(knitr)
library(tidyverse)
library(readxl)

set.seed(42)
```

# Overview

## Dependent Variables

**Primary DV**: **Trust Change** (Decision 2 - Decision 1)

- Used in RQ1 and RQ4
- Measures how evaluators update their trust after observing an outcome

**Secondary DVs**:

- **Absolute Endorsement Strength** (RQ2): |Rating - 50|, measures sponsor endorsement behavior
- **Initial Trust** (RQ3): Decision 1 trust, measures evaluator's baseline response to endorsements

## Study Design

Each evaluator sees ONE sponsor making TWO decisions:

1. **Decision 1**: Evaluator sees sponsor endorsement (with strength) → stakes X% trust → learns outcome (success/failure)
2. **Decision 2**: SAME evaluator sees SAME sponsor on new candidate → stakes Y% trust
3. **Trust Change = Y% - X%**

## Research Questions

- **RQ1/HQ1**: Are female sponsors punished **more** for failures and rewarded **less** for successes?
- **RQ2/HQ2**: Do female sponsors provide **weaker** endorsements than male sponsors?
- **RQ3/HQ3**: Do female sponsors need **higher** endorsement strength to achieve same initial trust?
- **RQ4/HQ4**: Is trust change **more** contingent on endorsement strength × outcome for female sponsors?

\newpage


```{r generate-data}
# Parameters
n_sponsors <- 100
n_decisions_per_sponsor <- 10
n_evaluators <- 600

# STAGE 2: Sponsor Endorsement Decisions
sponsors <- data.frame(
  sponsor_id = 1:n_sponsors,
  sponsor_female = sample(0:1, n_sponsors, replace = TRUE)
)

# Load candidate data
candidates <- read_excel("candidates.xlsx")
n_cand <- nrow(candidates)
candidates <- candidates %>%
  mutate(
    gender_label = ifelse(gen == 1, "Male", "Female"),
    gk_percentile = rank(generalknowledge) / n_cand * 100,
    words_percentile = rank(wordpuzzles) / n_cand * 100,
    logic_percentile = rank(matrices) / n_cand * 100
  )

# Generate sponsor decisions (Stage 2)
stage2 <- expand.grid(
  sponsor_id = 1:n_sponsors,
  decision_num = 1:n_decisions_per_sponsor
) %>%
  left_join(sponsors, by = "sponsor_id") %>%
  rowwise() %>%
  mutate(
    # Sample candidates
    cand_a_id = sample(1:n_cand, 1),
    cand_b_id = sample(setdiff(1:n_cand, cand_a_id), 1),
    cand_a_gender = candidates$gender_label[cand_a_id],
    cand_b_gender = candidates$gender_label[cand_b_id],
    cand_a_perf = (candidates$gk_percentile[cand_a_id] + candidates$words_percentile[cand_a_id]) / 2,
    cand_b_perf = (candidates$gk_percentile[cand_b_id] + candidates$words_percentile[cand_b_id]) / 2,
    perf_diff = cand_a_perf - cand_b_perf,

    # Determine objectively better candidate (for gender effects)
    better_cand = ifelse(perf_diff > 0, "A", "B"),
    better_cand_female = ifelse(better_cand == "A",
                                ifelse(cand_a_gender == "Female", 1, 0),
                                ifelse(cand_b_gender == "Female", 1, 0)),

    # ENDORSEMENT STRENGTH on 0-100 scale (50 = neutral, >50 = A, <50 = B)
    # HQ2: Female sponsors provide 25% weaker endorsements (closer to 50)

    # Generate ABSOLUTE strength with realistic distribution (bell curve centered ~25)
    # Most people have moderate signal, fewer have very weak or very strong
    base_abs_strength = abs(rnorm(1, 25, 10)),  # Mean=25, SD=10, creates bell curve

    # Gender effects: "weaker" means SMALLER deviation from neutral (multiplicative)
    # This shrinks endorsements toward 50, regardless of direction
    strength_multiplier = (1 - 0.25 * sponsor_female) *               # Female sponsor: 25% weaker
                         (1 - 0.10 * better_cand_female) *            # Female candidate: 10% weaker
                         (1 - 0.06 * sponsor_female * better_cand_female),  # Interaction

    # Apply gender effects and bound
    abs_strength_adjusted = pmin(48, base_abs_strength * strength_multiplier),

    # Direction: better candidate gets the endorsement
    # Add small noise based on performance difference to make it more realistic
    perf_noise = 2 * (perf_diff / max(abs(perf_diff), 1)),  # Small adjustment based on actual perf
    strength_raw = 50 + (abs_strength_adjusted + perf_noise) * sign(perf_diff),
    strength = pmax(5, pmin(95, strength_raw)),

    # Endorsed candidate is determined BY the strength value
    endorsed_cand = ifelse(strength > 50, "A",
                          ifelse(strength < 50, "B",
                                sample(c("A", "B"), 1))),  # Tie-breaker at exactly 50
    protege_female = ifelse(endorsed_cand == "A",
                           ifelse(cand_a_gender == "Female", 1, 0),
                           ifelse(cand_b_gender == "Female", 1, 0)),

    # Outcome (based on actual logic performance)
    logic_pct = ifelse(endorsed_cand == "A",
                      candidates$logic_percentile[cand_a_id],
                      candidates$logic_percentile[cand_b_id]),
    outcome_prob = plogis(-2 + 0.05 * logic_pct),
    outcome = rbinom(1, 1, outcome_prob),
    outcome_label = ifelse(outcome == 1, "Success", "Failure")
  ) %>%
  ungroup()

# STAGE 3: Evaluator Trust Decisions (Within-Subject)
stage3 <- data.frame(
  evaluator_id = 1:n_evaluators
) %>%
  rowwise() %>%
  mutate(
    # Sample ONE sponsor
    sponsor_id = sample(unique(stage2$sponsor_id), 1),
    sponsor_female = sponsors$sponsor_female[sponsor_id],

    # Sample TWO decisions from this sponsor
    avail_decisions = list(which(stage2$sponsor_id == sponsor_id)),
    d1_idx = ifelse(length(avail_decisions[[1]]) >= 2,
                   sample(avail_decisions[[1]], 1),
                   avail_decisions[[1]][1]),
    d2_idx = ifelse(length(avail_decisions[[1]]) >= 2,
                   sample(setdiff(avail_decisions[[1]], d1_idx), 1),
                   avail_decisions[[1]][min(2, length(avail_decisions[[1]]))]),

    # Decision 1 characteristics
    strength_d1 = stage2$strength[d1_idx],
    outcome_d1 = stage2$outcome[d1_idx],
    outcome_d1_label = stage2$outcome_label[d1_idx],

    # Decision 2 characteristics
    strength_d2 = stage2$strength[d2_idx],
    outcome_d2 = stage2$outcome[d2_idx],

    # ABSOLUTE STRENGTH (distance from neutral)
    # Captures how strong the endorsement is, regardless of direction
    # 50 = neutral/weak, 0 or 100 = very strong
    abs_strength_d1 = abs(strength_d1 - 50),
    abs_strength_d2 = abs(strength_d2 - 50),

    # INITIAL TRUST (Decision 1) - HQ3
    # Evaluators stake 0-100% of their $2 bonus on the endorser
    # Based ONLY on the endorsement strength they observe (no prior gender bias)
    # HQ3: Females need HIGHER strength to achieve same trust (modeled as SLIGHTLY SHALLOWER slope)
    # Both lines start at same intercept, small slope difference for HQ3
    trust_d1_raw =
      15 +                                           # Same baseline for everyone at abs_strength=0
      1.4 * abs_strength_d1 +                        # Males: 1.4% trust per point of strength
      -0.15 * abs_strength_d1 * sponsor_female +     # Females: slightly shallower slope (1.4-0.15=1.25% per point)
      rnorm(1, 0, 8),                                # Larger variance for better visualization
    trust_d1 = pmax(0, pmin(100, trust_d1_raw)),

    # TRUST CHANGE (Decision 2 - Decision 1) - HQ1, HQ4
    # Simple linear model: trust_change = slope * abs_strength
    # At strength = 0: all lines start near 0 (no signal)
    # As strength increases: different slopes for each gender × outcome

    # HQ1 + HQ4: Each gender × outcome gets its own slope
    trust_change_slope = case_when(
      # Males: STEEP positive for success, nearly FLAT for failure
      sponsor_female == 0 & outcome_d1 == 1 ~ 1.0,      # Male success: steep upward
      sponsor_female == 0 & outcome_d1 == 0 ~ -0.2,     # Male failure: nearly flat

      # Females: MODERATE positive for success, VERY STEEP negative for failure
      sponsor_female == 1 & outcome_d1 == 1 ~ 0.4,      # Female success: moderate upward
      sponsor_female == 1 & outcome_d1 == 0 ~ -1.4      # Female failure: steep downward
    ),

    # Calculate trust change as simple linear function
    trust_change = trust_change_slope * abs_strength_d1 + rnorm(1, 0, 6),

    # Calculate trust_d2 for potential use elsewhere (with bounds)
    trust_d2_raw = trust_d1 + trust_change,
    trust_d2 = pmax(0, pmin(100, trust_d2_raw))
  ) %>%
  ungroup() %>%
  mutate(
    sponsor_gender = ifelse(sponsor_female == 1, "Female", "Male"),
    sponsor_gender_f = factor(sponsor_gender, levels = c("Male", "Female")),
    outcome_d1_f = factor(outcome_d1_label, levels = c("Failure", "Success"))
  )

# Prepare RQ datasets
rq1_data <- stage3
rq2_data <- stage2 %>%
  mutate(
    sponsor_gender_f = factor(ifelse(sponsor_female == 1, "Female", "Male"),
                             levels = c("Male", "Female")),
    protege_gender_f = factor(ifelse(protege_female == 1, "Female", "Male"),
                             levels = c("Male", "Female")),
    abs_strength = abs(strength - 50)  # Absolute endorsement strength
  )
rq3_data <- stage3
rq4_data <- stage3 %>%
  mutate(abs_strength_d1_c = abs_strength_d1 - mean(abs_strength_d1, na.rm = TRUE))
```

\newpage

# RQ1: Trust Change by Sponsor Gender × Protege Outcome

**Hypothesis (HQ1)**: Female sponsors are punished **more** for failures and rewarded **less** for successes.

## Model

$$
\begin{aligned}
\text{TrustChange}_{i} = \beta_0 &+ \beta_1 \text{Female}_{i} + \beta_2 \text{Success}_{i} \\
&+ \beta_3 (\text{Female}_{i} \times \text{Success}_{i}) + \epsilon_{i}
\end{aligned}
$$

where:

- $\text{TrustChange}_{i}$ = Trust in Decision 2 - Trust in Decision 1
- $\text{Female}_{i}$ = 1 if sponsor is female, 0 if male
- $\text{Success}_{i}$ = 1 if Decision 1 succeeded, 0 if failed
- $\beta_3$ tests HQ1: negative $\beta_3$ means females are punished more/rewarded less

```{r rq1-model, results='markup'}
model_rq1 <- lm(trust_change ~ sponsor_gender_f * outcome_d1_f, data = rq1_data)
summary(model_rq1)
```


## Interpretation

This model tests whether trust change (Decision 2 - Decision 1) differs by sponsor gender and Decision 1 outcome.

- The main effect of `sponsor_gender_fFemale` shows the baseline difference in how females are treated after failures
- The main effect of `outcome_d1_fSuccess` shows how much trust increases for males after success
- The interaction shows whether the success-boost is SMALLER for females

\newpage

## Visualization

```{r rq1-fig, fig.height=5, fig.cap="RQ1: Trust Change by Sponsor Gender and Decision 1 Outcome"}
plot_data_rq1 <- rq1_data %>%
  group_by(sponsor_gender_f, outcome_d1_f) %>%
  summarise(
    mean_change = mean(trust_change),
    se = sd(trust_change) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(plot_data_rq1,
       aes(x = outcome_d1_f, y = mean_change, fill = sponsor_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_change - se, ymax = mean_change + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = sprintf("%.1f", mean_change)),
            position = position_dodge(0.8),
            vjust = ifelse(plot_data_rq1$mean_change > 0, 1.5, -0.5),
            size = 6, color = "white", fontface = "bold") +
  scale_fill_manual(values = c("Male" = "#011F5B", "Female" = "#990000")) +
  scale_y_continuous(limits = c(-55, 35), breaks = seq(-50, 30, 10)) +
  labs(
    title = "RQ1: Are Female Sponsors Punished More and Rewarded Less?",
    subtitle = "Trust Change from Decision 1 to Decision 2",
    x = "Decision 1 Outcome",
    y = "Change in Trust (%)",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 13)
  )
```


\newpage

# RQ2: Endorsement Strength by Sponsor Gender × Protege Gender

**Hypothesis (HQ2)**: Female sponsors provide **weaker** endorsements (~25% less) than male sponsors.

## Model

$$
\begin{aligned}
\text{AbsStrength}_{ij} = \beta_0 &+ \beta_1 \text{FemaleSponsor}_{i} + \beta_2 \text{FemaleProtege}_{j} \\
&+ \beta_3 (\text{FemaleSponsor}_{i} \times \text{FemaleProtege}_{j}) + \epsilon_{ij}
\end{aligned}
$$

where:

- $\text{AbsStrength}_{ij}$ = Absolute endorsement strength = $|\text{Rating} - 50|$ (0=neutral, 50=max)
- $\text{FemaleSponsor}_{i}$ = 1 if sponsor is female, 0 if male
- $\text{FemaleProtege}_{j}$ = 1 if endorsed candidate is female, 0 if male
- $\beta_1$ tests HQ2: negative $\beta_1$ means female sponsors give weaker (closer to neutral) endorsements

\newpage


```{r rq2-model, results='markup'}
model_rq2 <- lm(abs_strength ~ sponsor_gender_f * protege_gender_f, data = rq2_data)
summary(model_rq2)
```


\newpage

## Visualization

```{r rq2-fig, fig.height=5, fig.width=9, fig.cap="RQ2: Absolute Endorsement Strength by Sponsor and Protege Gender"}
plot_data_rq2 <- rq2_data %>%
  group_by(sponsor_gender_f, protege_gender_f) %>%
  summarise(
    mean_abs_strength = mean(abs_strength),
    se = sd(abs_strength) / sqrt(n()),
    .groups = "drop"
  )

ggplot(plot_data_rq2,
       aes(x = sponsor_gender_f, y = mean_abs_strength, fill = protege_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_abs_strength - se, ymax = mean_abs_strength + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_text(aes(label = sprintf("%.1f", mean_abs_strength)),
            position = position_dodge(0.8),
            vjust = 1.5, size = 5, color = "white", fontface = "bold") +
  scale_fill_manual(values = c("Male" = "#011F5B", "Female" = "#990000"),
                    name = "Protege Gender") +
  scale_y_continuous(limits = c(0, 35), breaks = seq(0, 35, 5)) +
  labs(
    title = "RQ2: Do Female Sponsors Provide Weaker Endorsements?",
    subtitle = "Mean Absolute Endorsement Strength by Sponsor and Protege Gender",
    x = "Sponsor Gender",
    y = "Absolute Endorsement Strength (|Rating - 50|)"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 13)
  )
```


\newpage

# RQ3: Initial Trust by Sponsor Gender × Endorsement Strength

**Hypothesis (HQ3)**: Female sponsors need **higher** endorsement strength to achieve same initial trust as males.

## Model

$$
\begin{aligned}
\text{InitialTrust}_{i} = \beta_0 &+ \beta_1 \text{Female}_{i} + \beta_2 \text{AbsStrength}_{i} \\
&+ \beta_3 (\text{Female}_{i} \times \text{AbsStrength}_{i}) + \epsilon_{i}
\end{aligned}
$$

where:

- $\text{InitialTrust}_{i}$ = Evaluator's initial trust in Decision 1 (0-100%)
- $\text{Female}_{i}$ = 1 if sponsor is female, 0 if male
- $\text{AbsStrength}_{i}$ = Absolute endorsement strength = $|\text{Rating} - 50|$ (0=neutral, 50=very strong)
- $\beta_1$ < 0: Female sponsors start with lower baseline trust
- $\beta_3$ > 0: Females have steeper slope (need higher strength to catch up)


\newpage

```{r rq3-model, results='markup'}
model_rq3 <- lm(trust_d1 ~ sponsor_gender_f * abs_strength_d1, data = rq3_data)
summary(model_rq3)
```

\newpage

## Interpretation

This model tests initial trust (Decision 1) as function of sponsor gender and **absolute** endorsement strength.

**Key coefficients**:

- `sponsor_gender_fFemale`: Shows baseline trust penalty for females (negative)
- `sponsor_gender_fFemale:abs_strength_d1`: Shows whether females benefit **more** from higher strength (positive) ✓ **HQ3 prediction**

\newpage

## Visualization

```{r rq3-fig, fig.height=6, fig.cap="RQ3: Initial Trust by Sponsor Gender and Absolute Endorsement Strength"}
# Create prediction lines using the theoretical model parameters
# Both lines start at same intercept (15), different slopes (1.4 vs 1.25)
pred_data_rq3 <- expand.grid(
  abs_strength_d1 = seq(0, 50, by = 1),
  sponsor_gender_f = factor(c("Male", "Female"), levels = c("Male", "Female"))
) %>%
  mutate(
    # TRUE data-generating model: same intercept, different slopes
    trust_d1_pred = 15 +
      1.4 * abs_strength_d1 +                              # Male slope
      -0.15 * abs_strength_d1 * (sponsor_gender_f == "Female")  # Female slope reduction
  )

# Show continuous distribution with theoretical prediction lines
ggplot(rq3_data,
       aes(x = abs_strength_d1, y = trust_d1,
           color = sponsor_gender_f, fill = sponsor_gender_f)) +
  geom_point(alpha = 0.3, size = 1.5) +
  # Use theoretical predictions instead of geom_smooth
  geom_line(data = pred_data_rq3,
            aes(y = trust_d1_pred),
            size = 1.5) +
  scale_color_manual(values = c("Male" = "#011F5B", "Female" = "#990000")) +
  scale_fill_manual(values = c("Male" = "#011F5B", "Female" = "#990000")) +
  scale_x_continuous(breaks = seq(0, 50, 10), limits = c(0, 50)) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "RQ3: Do Female Sponsors Need Higher Strength to Achieve Same Trust?",
    subtitle = "Initial Trust (Decision 1) by Absolute Endorsement Strength",
    x = "Absolute Endorsement Strength (|Rating - 50|)",
    y = "Initial Trust (%)",
    color = "Sponsor Gender",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13),
    panel.grid.minor.x = element_blank()
  )
```

**Expected pattern (HQ3):**

- At **abs_strength = 0**: Both lines start at **same point** (no prior gender bias)
- At **low strength**: Small gap
- At **higher strength**: Gap **widens** (males trusted more - females have shallower slope)


\newpage

# RQ4: Trust Change by Gender × Strength × Outcome (3-Way Interaction)

**Hypothesis (HQ4)**: Trust change is **more** contingent on endorsement strength × outcome for female sponsors.

## Model

$$
\begin{aligned}
\text{TrustChange}_{i} = \beta_0 &+ \beta_1 \text{Female}_{i} + \beta_2 \text{AbsStrength}_{i}^{c} + \beta_3 \text{Success}_{i} \\
&+ \beta_4 (\text{Female}_{i} \times \text{AbsStrength}_{i}^{c}) \\
&+ \beta_5 (\text{Female}_{i} \times \text{Success}_{i}) \\
&+ \beta_6 (\text{AbsStrength}_{i}^{c} \times \text{Success}_{i}) \\
&+ \beta_7 (\text{Female}_{i} \times \text{AbsStrength}_{i}^{c} \times \text{Success}_{i}) + \epsilon_{i}
\end{aligned}
$$

where:

- $\text{TrustChange}_{i}$ = Trust in Decision 2 - Trust in Decision 1
- $\text{Female}_{i}$ = 1 if sponsor is female, 0 if male
- $\text{AbsStrength}_{i}^{c}$ = Absolute endorsement strength (mean-centered)
- $\text{Success}_{i}$ = 1 if Decision 1 succeeded, 0 if failed
- $\beta_7$ tests HQ4: positive $\beta_7$ means strength × outcome interaction is **stronger** for females

\newpage

```{r rq4-model, results='markup'}
model_rq4 <- lm(trust_change ~ sponsor_gender_f * abs_strength_d1_c * outcome_d1_f,
                data = rq4_data)
summary(model_rq4)
```

\newpage

## Interpretation

This model tests the 3-way interaction: Does the endorsement strength × outcome effect differ by sponsor gender?

**Key coefficient**: `sponsor_gender_fFemale:abs_strength_d1_c:outcome_d1_fSuccess` (3-way interaction)

- If **positive**: Female sponsors show **stronger** strength × outcome interaction ✓ **HQ4 prediction**
- Meaning: Outcomes matter **more** for females when they made strong vs. weak endorsements


## Visualization

```{r rq4-fig, fig.height=6, fig.width=11, fig.cap="RQ4: Trust Change by Sponsor Gender, Absolute Endorsement Strength, and Outcome"}
# Create prediction lines using the theoretical model parameters
# Different intercepts and slopes for each gender × outcome combination
pred_data_rq4 <- expand.grid(
  abs_strength_d1 = seq(0, 50, by = 1),
  sponsor_gender_f = factor(c("Male", "Female"), levels = c("Male", "Female")),
  outcome_d1_f = factor(c("Success", "Failure"), levels = c("Failure", "Success"))
) %>%
  mutate(
    # Simple linear model: each gender × outcome gets its own slope
    trust_change_slope = case_when(
      sponsor_gender_f == "Male" & outcome_d1_f == "Success" ~ 1.0,      # Male success: steep up
      sponsor_gender_f == "Male" & outcome_d1_f == "Failure" ~ -0.2,     # Male failure: nearly flat
      sponsor_gender_f == "Female" & outcome_d1_f == "Success" ~ 0.4,    # Female success: moderate up
      sponsor_gender_f == "Female" & outcome_d1_f == "Failure" ~ -1.4    # Female failure: steep down
    ),

    # Calculate predicted trust change
    trust_change_pred = trust_change_slope * abs_strength_d1
  )

# Show continuous distribution with theoretical prediction lines
ggplot(rq4_data,
       aes(x = abs_strength_d1, y = trust_change,
           color = outcome_d1_f, fill = outcome_d1_f)) +
  geom_point(alpha = 0.2, size = 1) +
  # Use theoretical predictions instead of geom_smooth
  geom_line(data = pred_data_rq4,
            aes(y = trust_change_pred),
            size = 1.5) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  facet_wrap(~ sponsor_gender_f, nrow = 1) +
  scale_color_manual(values = c("Failure" = "#C62828", "Success" = "#2E7D32"),
                     labels = c("D1 Failed", "D1 Succeeded")) +
  scale_fill_manual(values = c("Failure" = "#C62828", "Success" = "#2E7D32"),
                    labels = c("D1 Failed", "D1 Succeeded")) +
  scale_x_continuous(breaks = seq(0, 50, 10), limits = c(0, 50)) +
  scale_y_continuous(limits = c(-70, 50), breaks = seq(-70, 50, 10)) +
  labs(
    title = "RQ4: Is Trust Change More Sensitive to Strength × Outcome for Females?",
    x = "Absolute Endorsement Strength (|Rating - 50|)",
    y = "Trust Change (percentage points)",
    color = "D1 Outcome",
    fill = "D1 Outcome"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    strip.text = element_text(size = 13, face = "bold"),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13)
  )
```

\newpage

**Expected pattern (HQ4):**

**Key insight**: At **low endorsement strength (< 12-15)**, all lines should be **near zero** - minimal trust change when there's no signal to update on.

**Male Sponsors:**

- Both lines start **near 0** at low strength (no confidence in signal)
- **Success line (green)**: **Steep upward** curve - stronger endorsements lead to much greater trust gains
- **Failure line (red)**: Moderate downward curve - stronger endorsements lead to moderate trust losses
- Lines **diverge** as strength increases, driven primarily by **success rewards**

**Female Sponsors:**

- Both lines start **near 0** at low strength (no confidence in signal)
- **Success line (green)**: Moderate upward curve - stronger endorsements lead to modest trust gains
- **Failure line (red)**: **Very steep downward** curve - stronger endorsements lead to dramatically greater trust losses
- Lines **diverge more dramatically** than males, driven primarily by **failure punishments**

**HQ4:** The **strength × outcome interaction is stronger for females** because:

- When female sponsors make **strong endorsements that fail**, they are punished **much more severely** (steeper negative slope)
- Male sponsors show the **opposite asymmetry**: they are **rewarded more** for strong successful endorsements (steeper positive slope)
- At low strength, the gender difference is minimal (both near 0)
- At high strength, the gender asymmetry becomes pronounced



