---
title: "Stage 3 Results — Strong-Only Pilot (N=400)"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document:
    toc: no
    fig_caption: true
    latex_engine: pdflatex
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    code_folding: hide
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6
)

library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)

is_pdf <- knitr::is_latex_output()
if (!is_pdf) library(kableExtra)

styled_kable <- function(data, ...) {
  k <- kable(data, booktabs = TRUE, ...)
  if (!is_pdf) k <- kable_styling(k, bootstrap_options = c("striped", "condensed"), full_width = FALSE)
  k
}

PENN_BLUE   <- "#011F5B"
PENN_RED    <- "#990000"
SUCCESS_GRN <- "#2E7D32"
FAILURE_RED <- "#C62828"

# Strong-only Prolific study
TARGET_STUDY <- "699c9e56d324339355fee87e"
```

```{r load-data, include=FALSE}
raw <- read.csv("../output/stage3_strong_only_data.csv", stringsAsFactors = FALSE)
raw <- raw[-c(1, 2), ]

numeric_cols <- c("Progress", "Duration..in.seconds.", "Finished",
                  "endorser_slider_value_q1", "endorser_slider_value_q2",
                  "stake_percent_q1", "stake_percent_q2",
                  "rt_ms_stage3_q1", "rt_ms_stage3_q2", "rt_ms_stage3_outcome",
                  "stage3_q1_is_correct", "stage3_q1_actual_bonus",
                  "age", "gender", "race")
for (col in numeric_cols) {
  if (col %in% names(raw)) raw[[col]] <- suppressWarnings(as.numeric(raw[[col]]))
}

raw$StartDate <- as.POSIXct(raw$StartDate, format = "%Y-%m-%d %H:%M:%S")
raw$date <- as.Date(raw$StartDate)

# Exclusion cascade
d0 <- raw
d1 <- d0 %>% filter(Status != "1")
d2 <- d1 %>% filter(Finished == 1)
d3 <- d2 %>% filter(!is.na(PROLIFIC_PID) & trimws(PROLIFIC_PID) != "")
d3b <- d3 %>% filter(STUDY_ID == TARGET_STUDY)
d4 <- d3b %>% filter(Q42 == "2")
d5 <- d4 %>% filter(!is.na(assigned_condition) & trimws(assigned_condition) != "")
d6 <- d5 %>% filter(!is.na(stake_percent_q1))
df <- d6

# Derive variables
df <- df %>%
  mutate(
    endorser_gender_code = ifelse(grepl("^M_", assigned_condition), "Man", "Woman"),
    endorser_correct     = ifelse(grepl("_correct_", assigned_condition), 1, 0),
    endorser_gender_f = factor(endorser_gender_code, levels = c("Man", "Woman")),
    outcome_f         = factor(ifelse(stage3_q1_is_correct == 1, "Success", "Failure"),
                               levels = c("Failure", "Success")),
    trust_change = stake_percent_q2 - stake_percent_q1,
    duration_min = Duration..in.seconds. / 60
  )

df <- df %>%
  mutate(
    abs_strength_q1 = abs(endorser_slider_value_q1 - 50),
    abs_strength_q2 = abs(endorser_slider_value_q2 - 50)
  )

df_tc <- df %>%
  filter(!is.na(trust_change), !is.na(stake_percent_q2)) %>%
  mutate(
    abs_strength_q1_c = abs_strength_q1 - mean(abs_strength_q1, na.rm = TRUE),
    abs_strength_q2_c = abs_strength_q2 - mean(abs_strength_q2, na.rm = TRUE),
    congruent_update = ifelse(
      (outcome_f == "Success" & trust_change > 0) |
      (outcome_f == "Failure" & trust_change < 0),
      1, 0
    )
  )

# Manipulation check subsets
df$q44_resp <- case_when(df$Q44 == "1" ~ "Man", df$Q44 == "2" ~ "Woman", TRUE ~ NA_character_)
df_pass <- df %>% filter(q44_resp == endorser_gender_code)
df_pass_tc <- df_pass %>%
  filter(!is.na(trust_change), !is.na(stake_percent_q2)) %>%
  mutate(
    abs_strength_q1_c = abs_strength_q1 - mean(abs_strength_q1, na.rm = TRUE),
    abs_strength_q2_c = abs_strength_q2 - mean(abs_strength_q2, na.rm = TRUE),
    congruent_update = ifelse(
      (outcome_f == "Success" & trust_change > 0) |
      (outcome_f == "Failure" & trust_change < 0),
      1, 0
    )
  )

# Helper functions
safe_coef <- function(model, term) {
  cf <- coef(model)
  if (term %in% names(cf)) round(cf[term], 3) else NA
}
safe_p <- function(model, term) {
  s <- summary(model)$coefficients
  if (term %in% rownames(s)) round(s[term, 4], 3) else NA
}
```

# Data Overview

## Data Freshness

```{r data-freshness}
cat("Data exported:", format(file.info("../output/stage3_strong_only_data.csv")$mtime, "%Y-%m-%d %H:%M"), "\n")
cat("Analysis run:", format(Sys.time(), "%Y-%m-%d %H:%M"), "\n")
cat("Total raw rows:", nrow(d0), "\n")
```

## Exclusion Cascade

```{r exclusion-cascade}
cascade <- data.frame(
  Step = c("Raw responses", "Not preview (Status != 1)", "Finished",
           "Has Prolific PID", "Target study",
           "Comprehension check (Q42 = 2)",
           "Has assigned condition", "Has Q1 stake"),
  N = c(nrow(d0), nrow(d1), nrow(d2), nrow(d3), nrow(d3b), nrow(d4), nrow(d5), nrow(d6)),
  Dropped = c(NA, nrow(d0) - nrow(d1), nrow(d1) - nrow(d2), nrow(d2) - nrow(d3),
              nrow(d3) - nrow(d3b), nrow(d3b) - nrow(d4), nrow(d4) - nrow(d5),
              nrow(d5) - nrow(d6))
)
styled_kable(cascade, col.names = c("Filter Step", "N Remaining", "Dropped"), row.names = FALSE)
```

```{r comprehension-flag}
comp_rate <- round(nrow(d4) / nrow(d3b) * 100, 1)
cat("Comprehension check pass rate:", comp_rate, "%\n")
if (comp_rate < 60) {
  cat("WARNING: Pass rate is notably lower than the original N=400 study (87.3%).\n")
  cat("This may indicate participant pool quality differences or survey variation.\n")
}
```

## Sample Summary

```{r sample-summary}
cat("Prolific Study ID:", TARGET_STUDY, "\n")
cat("Survey: SV_6oqgEjZV4MhmbiK (strong-only)\n")
cat("Date range:", format(min(df$StartDate, na.rm = TRUE), "%b %d"),
    "to", format(max(df$StartDate, na.rm = TRUE), "%b %d, %Y"), "\n")
cat("Usable N:", nrow(df), "\n")
cat("Has Trust Change:", sum(!is.na(df$trust_change)), "\n")
cat("Mean duration:", round(mean(df$duration_min, na.rm = TRUE), 1), "min\n")
cat("Mean Q1 Stake:", round(mean(df$stake_percent_q1), 1), "\n")
cat("Mean Q2 Stake:", round(mean(df$stake_percent_q2, na.rm = TRUE), 1), "\n")
cat("Mean Trust Change:", round(mean(df$trust_change, na.rm = TRUE), 1), "\n")
```

## Condition Balance

```{r condition-balance}
cond_tab <- df %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(N = n(), .groups = "drop") %>%
  arrange(endorser_gender_f, outcome_f)

styled_kable(cond_tab,
             col.names = c("Sponsor Gender", "Outcome", "N"),
             row.names = FALSE)
```

## Design Note

This is a **strong-only** replication of the strong endorsement condition from the original N=400 pilot (Feb 19 study). The design is a **2 $\times$ 2 between-subjects** factorial:

- **Endorser Gender**: Man vs. Woman
- **Outcome**: Failure (incorrect) vs. Success (correct)

All endorsements are strong ($>70$ on 0--100 slider). The primary hypothesis (from the original N=400 analysis) is that women receive a **smaller success boost** than men in the strong condition --- a negative Gender $\times$ Outcome interaction.

**Expected effect**: In the original N=400 study (strong condition only, about 50/cell), the Gender $\times$ Outcome interaction was $b = -9.0$, $p = .226$. With about 100/cell here, we expected $p \approx .085$.

\newpage

# Primary Analysis: Trust Change by Sponsor Gender $\times$ Outcome

## Cell Means

```{r cell-means}
cell_means <- df_tc %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(
    N = n(),
    Mean_TC = round(mean(trust_change), 1),
    SD = round(sd(trust_change), 1),
    SE = round(sd(trust_change) / sqrt(n()), 1),
    .groups = "drop"
  ) %>%
  arrange(endorser_gender_f, outcome_f)

styled_kable(cell_means,
             col.names = c("Sponsor Gender", "Outcome", "N", "Mean Trust Change", "SD", "SE"),
             row.names = FALSE)
```

## Success Boost

```{r success-boost}
boost <- df_tc %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(mean_tc = mean(trust_change), .groups = "drop") %>%
  pivot_wider(names_from = outcome_f, values_from = mean_tc) %>%
  mutate(Success_Boost = round(Success - Failure, 1))

styled_kable(boost %>% select(endorser_gender_f, Failure, Success, Success_Boost) %>%
               mutate(Failure = round(Failure, 1), Success = round(Success, 1)),
             col.names = c("Sponsor Gender", "Failure Mean", "Success Mean", "Success Boost"),
             row.names = FALSE)
```

## Model

$$
\text{trust\_change}_{i} = \beta_0 + \beta_1 \texttt{Woman}_{i} + \beta_2 \texttt{Success}_{i} + \beta_3 (\texttt{Woman}_{i} \times \texttt{Success}_{i}) + \epsilon_{i}
$$

```{r model-vars}
model_vars <- data.frame(
  Coefficient = c("Intercept", "Woman", "Success", "Woman x Success"),
  Meaning = c("Mean trust change: male sponsors after failure",
              "Gender difference in failure condition",
              "Success boost for male sponsors",
              "HQ1 test: negative = women's success boost is smaller")
)
styled_kable(model_vars, col.names = c("Term", "Interpretation"), row.names = FALSE)
```

```{r primary-model, results='markup'}
model_primary <- lm(trust_change ~ endorser_gender_f * outcome_f, data = df_tc)
summary(model_primary)
```

```{r primary-summary}
int_term <- "endorser_gender_fWoman:outcome_fSuccess"
b_int <- round(coef(model_primary)[int_term], 1)
p_int <- round(summary(model_primary)$coefficients[int_term, 4], 3)
b_success <- round(coef(model_primary)["outcome_fSuccess"], 1)
b_woman_success <- round(b_success + coef(model_primary)[int_term], 1)

cat("--- Summary ---\n")
cat("Man success boost:", b_success, "\n")
cat("Woman success boost:", b_woman_success, "\n")
cat("Gender x Outcome interaction: b =", b_int, ", p =", p_int, "\n")
cat("Original N=400 strong condition: b = -9.0, p = .226 (~50/cell)\n")
```

\newpage

## Visualization

```{r primary-fig, fig.height=6, fig.width=9, fig.cap="Trust Change by Sponsor Gender and Outcome (Strong Endorsements Only)"}
primary_stats <- df_tc %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(
    mean_change = mean(trust_change),
    se = sd(trust_change) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(primary_stats,
       aes(x = outcome_f, y = mean_change, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_change - se, ymax = mean_change + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_change, n),
                vjust = ifelse(mean_change >= 0, -0.5, 1.5)),
            position = position_dodge(0.8),
            size = 4, fontface = "bold", color = "black") +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(-25, 20), breaks = seq(-25, 20, 5)) +
  labs(
    title = "Trust Change by Sponsor Gender and Outcome (Strong Only)",
    subtitle = paste0("N = ", nrow(df_tc), " | All endorsements strong"),
    x = "Decision 1 Outcome",
    y = "Mean Change in Trust (%)",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13)
  )
```

\newpage

# Binary DV Robustness: Outcome-Congruent Update

```{r binary-model, results='markup'}
model_binary <- glm(congruent_update ~ endorser_gender_f * outcome_f +
                      abs_strength_q1_c + abs_strength_q2_c,
                    family = binomial(link = "logit"),
                    data = df_tc)
summary(model_binary)
```

```{r binary-fig, fig.height=5, fig.width=9, fig.cap="Binary DV: Outcome-congruent update rates"}
bin_stats <- df_tc %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(
    rate = mean(congruent_update),
    n = n(),
    .groups = "drop"
  )

ggplot(bin_stats,
       aes(x = outcome_f, y = rate, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%\n(n=%d)", 100 * rate, n)),
            position = position_dodge(0.8),
            vjust = -0.5, size = 3.5, fontface = "bold") +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1),
                     labels = function(x) paste0(round(100 * x), "%")) +
  labs(
    title = "Binary Robustness: Outcome-Congruent Trust Update",
    subtitle = paste0("1 = update direction matches outcome | N = ", nrow(df_tc)),
    x = "Decision 1 Outcome",
    y = "Congruent Update Rate",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13)
  )
```

\newpage

# Initial Trust (Decision 1) by Sponsor Gender

Since all endorsements are strong, we can test whether evaluators anchor differently by gender even before learning the outcome.

```{r q1-trust}
q1_stats <- df %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(
    N = n(),
    Mean_Q1 = round(mean(stake_percent_q1), 1),
    SD = round(sd(stake_percent_q1), 1),
    .groups = "drop"
  )

styled_kable(q1_stats,
             col.names = c("Sponsor Gender", "Outcome", "N", "Mean Q1 Stake", "SD"),
             row.names = FALSE)
```

```{r q1-model, results='markup'}
model_q1 <- lm(stake_percent_q1 ~ endorser_gender_f, data = df)
summary(model_q1)
```

```{r q1-fig, fig.height=5, fig.width=7, fig.cap="Initial Trust by Sponsor Gender (all strong endorsements)"}
q1_gender <- df %>%
  group_by(endorser_gender_f) %>%
  summarise(
    mean_trust = mean(stake_percent_q1),
    se = sd(stake_percent_q1) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(q1_gender,
       aes(x = endorser_gender_f, y = mean_trust, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", width = 0.6) +
  geom_errorbar(aes(ymin = mean_trust - se, ymax = mean_trust + se), width = 0.2) +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_trust, n)),
            vjust = 1.5, size = 5, color = "white", fontface = "bold") +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "Initial Trust by Sponsor Gender (All Strong Endorsements)",
    subtitle = paste0("N = ", nrow(df)),
    x = "Sponsor Gender",
    y = "Initial Trust (%)",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 13)
  )
```

\newpage

# Appendix: Manipulation Check Passers

Participants were asked to identify the sponsor's gender after the task (Q44). Overall accuracy was `r round(mean(df$q44_resp == df$endorser_gender_code, na.rm = TRUE) * 100, 1)`%. Below we re-run the primary analysis excluding those who failed or did not respond.

```{r manip-summary}
cat("Manipulation check pass: N =", nrow(df_pass), "of", nrow(df), "\n")
cat("  Man:", sum(df_pass$endorser_gender_code == "Man"),
    "| Woman:", sum(df_pass$endorser_gender_code == "Woman"), "\n")
cat("  Excluded:", nrow(df) - nrow(df_pass),
    "(Man:", sum(df$endorser_gender_code == "Man") - sum(df_pass$endorser_gender_code == "Man"),
    "| Woman:", sum(df$endorser_gender_code == "Woman") - sum(df_pass$endorser_gender_code == "Woman"), ")\n")

cat("\nQ44 non-response:", sum(is.na(df$q44_resp)), "of", nrow(df), "\n")
```

## Cell Means (Manipulation Check Passers)

```{r manip-cell-means}
cell_means_pass <- df_pass_tc %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(
    N = n(),
    Mean_TC = round(mean(trust_change), 1),
    SD = round(sd(trust_change), 1),
    SE = round(sd(trust_change) / sqrt(n()), 1),
    .groups = "drop"
  ) %>%
  arrange(endorser_gender_f, outcome_f)

styled_kable(cell_means_pass,
             col.names = c("Sponsor Gender", "Outcome", "N", "Mean Trust Change", "SD", "SE"),
             row.names = FALSE)
```

## Success Boost (Manipulation Check Passers)

```{r manip-success-boost}
boost_pass <- df_pass_tc %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(mean_tc = mean(trust_change), .groups = "drop") %>%
  pivot_wider(names_from = outcome_f, values_from = mean_tc) %>%
  mutate(Success_Boost = round(Success - Failure, 1))

styled_kable(boost_pass %>% select(endorser_gender_f, Failure, Success, Success_Boost) %>%
               mutate(Failure = round(Failure, 1), Success = round(Success, 1)),
             col.names = c("Sponsor Gender", "Failure Mean", "Success Mean", "Success Boost"),
             row.names = FALSE)
```

## Model (Manipulation Check Passers)

```{r manip-model, results='markup'}
model_pass <- lm(trust_change ~ endorser_gender_f * outcome_f, data = df_pass_tc)
summary(model_pass)
```

```{r manip-summary-stats}
b_int_p <- round(coef(model_pass)[int_term], 1)
p_int_p <- round(summary(model_pass)$coefficients[int_term, 4], 3)
b_success_p <- round(coef(model_pass)["outcome_fSuccess"], 1)
b_woman_success_p <- round(b_success_p + coef(model_pass)[int_term], 1)

cat("--- Manip Passers Summary ---\n")
cat("Man success boost:", b_success_p, "\n")
cat("Woman success boost:", b_woman_success_p, "\n")
cat("Gender x Outcome interaction: b =", b_int_p, ", p =", p_int_p, "\n")
```

## Visualization (Manipulation Check Passers)

```{r manip-fig, fig.height=6, fig.width=9, fig.cap="Trust Change --- Manipulation Check Passers Only"}
pass_stats <- df_pass_tc %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(
    mean_change = mean(trust_change),
    se = sd(trust_change) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(pass_stats,
       aes(x = outcome_f, y = mean_change, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_change - se, ymax = mean_change + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_change, n),
                vjust = ifelse(mean_change >= 0, -0.5, 1.5)),
            position = position_dodge(0.8),
            size = 4, fontface = "bold", color = "black") +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(-25, 20), breaks = seq(-25, 20, 5)) +
  labs(
    title = "Trust Change (Manipulation Check Passers Only)",
    subtitle = paste0("N = ", nrow(df_pass_tc), " | Strong endorsements only"),
    x = "Decision 1 Outcome",
    y = "Mean Change in Trust (%)",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13)
  )
```

## Binary DV (Manipulation Check Passers)

```{r manip-binary-model, results='markup'}
model_binary_pass <- glm(congruent_update ~ endorser_gender_f * outcome_f +
                           abs_strength_q1_c + abs_strength_q2_c,
                         family = binomial(link = "logit"),
                         data = df_pass_tc)
summary(model_binary_pass)
```

\newpage

# Comparison: Strong-Only Pilot vs. Original N=400 Strong Condition

```{r comparison-table}
# This table compares the current strong-only results with the
# strong condition subset from the original N=400 study
comp <- data.frame(
  Metric = c("N (usable)", "N (trust change)",
             "Man: Failure mean", "Man: Success mean", "Man: Success boost",
             "Woman: Failure mean", "Woman: Success mean", "Woman: Success boost",
             "Gender x Outcome b", "Gender x Outcome p"),
  Original_Strong = c("~190 (strong only)", "~190",
                       "-15.1", "-0.5", "+14.6",
                       "-12.0", "-6.4", "+5.6",
                       "-9.0", ".226"),
  Current_Strong = c(
    as.character(nrow(df_tc)),
    as.character(nrow(df_tc)),
    as.character(round(mean(df_tc$trust_change[df_tc$endorser_gender_f == "Man" & df_tc$outcome_f == "Failure"]), 1)),
    as.character(round(mean(df_tc$trust_change[df_tc$endorser_gender_f == "Man" & df_tc$outcome_f == "Success"]), 1)),
    as.character(round(mean(df_tc$trust_change[df_tc$endorser_gender_f == "Man" & df_tc$outcome_f == "Success"]) -
                       mean(df_tc$trust_change[df_tc$endorser_gender_f == "Man" & df_tc$outcome_f == "Failure"]), 1)),
    as.character(round(mean(df_tc$trust_change[df_tc$endorser_gender_f == "Woman" & df_tc$outcome_f == "Failure"]), 1)),
    as.character(round(mean(df_tc$trust_change[df_tc$endorser_gender_f == "Woman" & df_tc$outcome_f == "Success"]), 1)),
    as.character(round(mean(df_tc$trust_change[df_tc$endorser_gender_f == "Woman" & df_tc$outcome_f == "Success"]) -
                       mean(df_tc$trust_change[df_tc$endorser_gender_f == "Woman" & df_tc$outcome_f == "Failure"]), 1)),
    as.character(b_int),
    as.character(p_int)
  )
)

styled_kable(comp,
             col.names = c("", "Original N=400 (Strong)", "Strong-Only Pilot"),
             row.names = FALSE)
```

\newpage

# Summary of All Tests

```{r all-tests-summary}
int_term <- "endorser_gender_fWoman:outcome_fSuccess"

all_tests <- data.frame(
  Test = c("Gender x Outcome (Full)",
           "Gender x Outcome (Manip Passers)",
           "Binary: Gender x Outcome (Full)",
           "Binary: Gender x Outcome (Manip Passers)"),
  N = c(nrow(df_tc), nrow(df_pass_tc), nrow(df_tc), nrow(df_pass_tc)),
  b = c(safe_coef(model_primary, int_term),
        safe_coef(model_pass, int_term),
        safe_coef(model_binary, int_term),
        safe_coef(model_binary_pass, int_term)),
  p = c(safe_p(model_primary, int_term),
        safe_p(model_pass, int_term),
        safe_p(model_binary, int_term),
        safe_p(model_binary_pass, int_term))
)

styled_kable(all_tests,
             col.names = c("Test", "N", "Interaction b", "Interaction p"),
             row.names = FALSE)
```
