---
title: "Stage 3 Pilot Results — Sponsorship Network"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document:
    toc: no
    fig_caption: true
    latex_engine: pdflatex
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    code_folding: hide
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6
)

library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(lme4)
library(lmerTest)

is_pdf <- knitr::is_latex_output()
if (!is_pdf) library(kableExtra)

styled_kable <- function(data, ...) {
  k <- kable(data, booktabs = TRUE, ...)
  if (!is_pdf) k <- kable_styling(k, bootstrap_options = c("striped", "condensed"), full_width = FALSE)
  k
}

PENN_BLUE   <- "#011F5B"
PENN_RED    <- "#990000"
SUCCESS_GRN <- "#2E7D32"
FAILURE_RED <- "#C62828"

TARGET_STUDY <- "698e27db580428e78f8e9ff1"
```

```{r load-data, include=FALSE}
# --- Stage 3 data ---
raw <- read.csv("../output/stage3_pilot_data.csv", stringsAsFactors = FALSE)
raw <- raw[-c(1, 2), ]

numeric_cols <- c("Progress", "Duration..in.seconds.", "Finished",
                  "endorser_slider_value_q1", "endorser_slider_value_q2",
                  "stake_percent_q1", "stake_percent_q2",
                  "rt_ms_stage3_q1", "rt_ms_stage3_q2", "rt_ms_stage3_outcome",
                  "stage3_q1_is_correct", "stage3_q1_actual_bonus",
                  "age", "gender", "race")
for (col in numeric_cols) {
  if (col %in% names(raw)) raw[[col]] <- suppressWarnings(as.numeric(raw[[col]]))
}

# Exclusion cascade
d0 <- raw
d1 <- d0 %>% filter(Status != "1")
d2 <- d1 %>% filter(Finished == 1)
d3 <- d2 %>% filter(!is.na(PROLIFIC_PID) & trimws(PROLIFIC_PID) != "")
d3b <- d3 %>% filter(STUDY_ID == TARGET_STUDY)
d4 <- d3b %>% filter(Q42 == "2")
d5 <- d4 %>% filter(!is.na(assigned_condition) & trimws(assigned_condition) != "")
d6 <- d5 %>% filter(!is.na(stake_percent_q1))
df <- d6

# Derive variables
df <- df %>%
  mutate(
    endorser_gender_code = ifelse(grepl("^M_", assigned_condition), "Man", "Woman"),
    endorser_correct     = ifelse(grepl("_correct_", assigned_condition), 1, 0),
    endorser_strong      = ifelse(grepl("_strong$", assigned_condition), 1, 0),
    abs_strength_q1 = abs(endorser_slider_value_q1 - 50),
    abs_strength_q2 = abs(endorser_slider_value_q2 - 50),
    endorser_gender_f = factor(endorser_gender_code, levels = c("Man", "Woman")),
    correctness_f     = factor(ifelse(endorser_correct == 1, "Correct", "Incorrect"),
                               levels = c("Incorrect", "Correct")),
    strength_f        = factor(ifelse(endorser_strong == 1, "Strong", "Weak"),
                               levels = c("Weak", "Strong")),
    outcome_f         = factor(ifelse(stage3_q1_is_correct == 1, "Success", "Failure"),
                               levels = c("Failure", "Success")),
    trust_change = stake_percent_q2 - stake_percent_q1,
    duration_min = Duration..in.seconds. / 60
  )

df_tc <- df %>% filter(!is.na(trust_change))

# --- Stage 2 data ---
s2_raw <- read.csv("../output/stage2_main_data.csv", stringsAsFactors = FALSE)
s2_raw <- s2_raw[-c(1, 2), ]
s2_raw$Finished <- as.numeric(s2_raw$Finished)
s2_raw$StartDate <- as.POSIXct(s2_raw$StartDate, format = "%Y-%m-%d %H:%M:%S")
s2_raw$date <- as.Date(s2_raw$StartDate)

s2 <- s2_raw %>%
  filter(Status != "1", Finished == 1,
         !is.na(PROLIFIC_PID) & trimws(PROLIFIC_PID) != "",
         date >= as.Date("2026-02-12")) %>%
  filter(!is.na(t1_slider_value) & trimws(t1_slider_value) != "")

s2$endorser_gender <- case_when(
  s2$gender == "1" ~ "Woman", s2$gender == "2" ~ "Man", TRUE ~ "Other"
)

s2_long <- data.frame()
for (i in 1:10) {
  p <- paste0("t", i, "_")
  trial_df <- s2 %>%
    select(PROLIFIC_PID, endorser_gender,
           pair_id = !!paste0(p, "pair_id"), category = !!paste0(p, "category"),
           truth = !!paste0(p, "truth"), truth_gender = !!paste0(p, "truth_gender"),
           A_gender = !!paste0(p, "A_gender"), B_gender = !!paste0(p, "B_gender"),
           slider_value = !!paste0(p, "slider_value"),
           slider_side = !!paste0(p, "slider_side"),
           rt_ms = !!paste0(p, "rt_ms")) %>%
    mutate(trial = i)
  s2_long <- rbind(s2_long, trial_df)
}
s2_long$slider_value <- as.numeric(s2_long$slider_value)

s2_trials <- s2_long %>%
  filter(!is.na(slider_value), endorser_gender %in% c("Man", "Woman")) %>%
  mutate(
    abs_strength = abs(slider_value - 50),
    endorsed_side = ifelse(slider_value < 50, "A", ifelse(slider_value > 50, "B", "neutral")),
    endorsed_gender = case_when(
      endorsed_side == "A" ~ A_gender, endorsed_side == "B" ~ B_gender, TRUE ~ NA_character_
    ),
    is_correct = (endorsed_side == truth),
    endorser_gender_f = factor(endorser_gender, levels = c("Man", "Woman")),
    endorsed_gender_f = factor(endorsed_gender, levels = c("Man", "Woman"))
  )
```

## Dependent Variables

**Primary DV**: **Trust Change** (Decision 2 - Decision 1)

- Used in RQ1 and RQ4
- Measures how evaluators update their trust after observing an outcome

**Secondary DVs**:

- **Absolute Endorsement Strength** (RQ2): |Rating - 50|, measures sponsor endorsement behavior
- **Initial Trust** (RQ3): Decision 1 trust, measures evaluator's baseline response to endorsements

## Study Design

Each evaluator sees ONE sponsor making TWO decisions:

1. **Decision 1**: Evaluator sees sponsor endorsement (with strength) $\rightarrow$ stakes X% trust $\rightarrow$ learns outcome (success/failure)
2. **Decision 2**: SAME evaluator sees SAME sponsor on new candidate $\rightarrow$ stakes Y% trust
3. **Trust Change = Y% - X%**

## Research Questions

- **RQ1/HQ1**: Are female sponsors punished **more** for failures and rewarded **less** for successes?
- **RQ2/HQ2**: Do female sponsors provide **weaker** endorsements than male sponsors?
- **RQ3/HQ3**: Do female sponsors need **higher** endorsement strength to achieve same initial trust?
- **RQ4/HQ4**: Is trust change **more** contingent on endorsement strength $\times$ outcome for female sponsors?

```{r sample-desc}
# Manipulation check (used later in robustness)
df$q44_resp <- case_when(df$Q44 == "1" ~ "Man", df$Q44 == "2" ~ "Woman", TRUE ~ NA_character_)
```

\newpage

# RQ1: Trust Change by Sponsor Gender $\times$ Protege Outcome

**Hypothesis (HQ1)**: Female sponsors are punished **more** for failures and rewarded **less** for successes.

## Model

$$
\text{trust\_change}_{i} = \beta_0 + \beta_1 \texttt{Woman}_{i} + \beta_2 \texttt{Success}_{i} + \beta_3 (\texttt{Woman}_{i} \times \texttt{Success}_{i}) + \beta_4 \texttt{abs\_str\_q1\_c}_{i} + \beta_5 \texttt{abs\_str\_q2\_c}_{i} + \epsilon_{i}
$$

```{r rq1-vars}
rq1_vars <- data.frame(
  Coefficient = c("Woman", "Success", "Woman x Success", "abs_strength_q1_c", "abs_strength_q2_c"),
  R_Name = c("endorser_gender_fWoman", "outcome_fSuccess",
             "...fWoman:outcome_fSuccess", "abs_strength_q1_c", "abs_strength_q2_c"),
  Coding = c("Man = 0 (ref), Woman = 1", "Failure = 0 (ref), Success = 1",
             "Interaction term", "Mean-centered |Q1 slider - 50|",
             "Mean-centered |Q2 slider - 50|")
)
styled_kable(rq1_vars, col.names = c("Term", "Name in R output", "Coding"),
             row.names = FALSE)
```

- $\beta_3$ tests HQ1: negative $\beta_3$ means the success boost is **smaller** for female sponsors

```{r rq1-model, results='markup'}
df_tc <- df_tc %>%
  mutate(abs_strength_q1_c = abs_strength_q1 - mean(abs_strength_q1, na.rm = TRUE),
         abs_strength_q2_c = abs_strength_q2 - mean(abs_strength_q2, na.rm = TRUE))

model_rq1 <- lm(trust_change ~ endorser_gender_f * outcome_f + abs_strength_q1_c + abs_strength_q2_c,
                 data = df_tc)
summary(model_rq1)
```

## Interpretation

- **$\beta_0$ (Intercept)**: Mean trust change for **male sponsors after failure**, at average endorsement strength
- **$\beta_1$ (`endorser_gender_fWoman`)**: How much trust change differs for **female sponsors after failure** (relative to male)
- **$\beta_2$ (`outcome_fSuccess`)**: The success boost for **male sponsors** — how much more trust they get after success vs. failure
- **$\beta_3$ (`endorser_gender_fWoman:outcome_fSuccess`)**: **HQ1 test** — how much **smaller** (if negative) the success boost is for female sponsors
- **$\beta_4$ (`abs_strength_q1_c`)**: Controls for the pretreatment strength of the Q1 endorsement
- **$\beta_5$ (`abs_strength_q2_c`)**: Controls for the strength of the Q2 endorsement (different candidate pair)

\newpage

## Visualization

```{r rq1-fig, fig.height=5.5, fig.cap="RQ1: Trust Change by Sponsor Gender and Decision 1 Outcome"}
rq1_stats <- df_tc %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(
    mean_change = mean(trust_change),
    se = sd(trust_change) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(rq1_stats,
       aes(x = outcome_f, y = mean_change, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_change - se, ymax = mean_change + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_change, n),
                vjust = ifelse(mean_change >= 0, -0.5, 1.5)),
            position = position_dodge(0.8),
            size = 4, fontface = "bold", color = "black") +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(-25, 30), breaks = seq(-20, 30, 10)) +
  labs(
    title = "RQ1: Are Female Sponsors Punished More and Rewarded Less?",
    subtitle = paste0("Trust Change by Gender x Outcome (collapsed across Strength) | N = ", nrow(df_tc)),
    x = "Decision 1 Outcome",
    y = "Mean Change in Trust (%)",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 13)
  )
```

\newpage

# RQ2: Endorsement Strength by Sponsor Gender $\times$ Protege Gender

**Hypothesis (HQ2)**: Female sponsors provide **weaker** endorsements than male sponsors.

## Model

$$
\text{abs\_strength}_{ij} = \beta_0 + \beta_1 \texttt{Woman\_Sponsor}_{i} + \beta_2 \texttt{Woman\_Protege}_{j} + \beta_3 (\texttt{Woman\_Sponsor}_{i} \times \texttt{Woman\_Protege}_{j}) + u_{i} + \epsilon_{ij}
$$

```{r rq2-vars}
rq2_vars <- data.frame(
  Coefficient = c("Woman_Sponsor", "Woman_Protege", "Random intercept"),
  R_Name = c("endorser_gender_fWoman", "endorsed_gender_fWoman", "(1 | PROLIFIC_PID)"),
  Coding = c("Man = 0 (ref), Woman = 1", "Man = 0 (ref), Woman = 1",
             "10 trials per endorser")
)
styled_kable(rq2_vars, col.names = c("Term", "Name in R output", "Coding"),
             row.names = FALSE)
```

- $\beta_1$ tests HQ2: negative $\beta_1$ means female sponsors give weaker (closer to neutral) endorsements
- Mixed model with random intercepts accounts for 10 repeated trials per endorser

*This analysis uses Stage 2 main study data (N = `r n_distinct(s2_trials$PROLIFIC_PID)` endorsers, `r nrow(s2_trials)` trial observations).*

```{r rq2-model, results='markup'}
s2_model_data <- s2_trials %>% filter(!is.na(endorsed_gender_f))
model_rq2 <- lmer(abs_strength ~ endorser_gender_f * endorsed_gender_f + (1 | PROLIFIC_PID),
                   data = s2_model_data)
summary(model_rq2)
```

\newpage

## Visualization

```{r rq2-fig, fig.height=5, fig.width=9, fig.cap="RQ2: Absolute Endorsement Strength by Sponsor and Protege Gender"}
rq2_plot <- s2_trials %>%
  filter(!is.na(endorsed_gender_f)) %>%
  group_by(endorser_gender_f, endorsed_gender_f) %>%
  summarise(
    mean_abs_strength = mean(abs_strength),
    se = sd(abs_strength) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(rq2_plot,
       aes(x = endorser_gender_f, y = mean_abs_strength, fill = endorsed_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_abs_strength - se, ymax = mean_abs_strength + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_abs_strength, n)),
            position = position_dodge(0.8),
            vjust = 1.5, size = 4.5, color = "white", fontface = "bold") +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED),
                    name = "Protege Gender") +
  scale_y_continuous(limits = c(0, 45), breaks = seq(0, 45, 5)) +
  labs(
    title = "RQ2: Do Female Sponsors Provide Weaker Endorsements?",
    subtitle = paste0("Mean Absolute Endorsement Strength by Sponsor and Protege Gender | N = ",
                      n_distinct(s2_trials$PROLIFIC_PID), " endorsers"),
    x = "Sponsor Gender",
    y = "Absolute Endorsement Strength (|Rating - 50|)"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 13)
  )
```

\newpage

# RQ3: Initial Trust by Sponsor Gender $\times$ Endorsement Strength

**Hypothesis (HQ3)**: Female sponsors need **higher** endorsement strength to achieve same initial trust as males.

## Model

$$
\text{stake\_percent\_q1}_{i} = \beta_0 + \beta_1 \texttt{Woman}_{i} + \beta_2 \texttt{abs\_strength\_q1}_{i} + \beta_3 (\texttt{Woman}_{i} \times \texttt{abs\_strength\_q1}_{i}) + \epsilon_{i}
$$

```{r rq3-vars}
rq3_vars <- data.frame(
  Coefficient = c("DV: stake_percent_q1", "Woman", "abs_strength_q1", "Woman x Strength"),
  R_Name = c("stake_percent_q1", "endorser_gender_fWoman", "abs_strength_q1",
             "...fWoman:abs_strength_q1"),
  Coding = c("0-100 (evaluator initial trust)", "Man = 0 (ref), Woman = 1",
             "|slider - 50|; Weak ~ 1-2, Strong = 50", "Interaction term")
)
styled_kable(rq3_vars, col.names = c("Term", "Name in R output", "Coding"),
             row.names = FALSE)
```

- $\beta_2$: How much initial trust increases per unit of endorsement strength (for **male** sponsors)
- $\beta_3$ tests HQ3: negative $\beta_3$ means female sponsors have a **shallower** slope (need more strength for same trust)

```{r rq3-model, results='markup'}
model_rq3 <- lm(stake_percent_q1 ~ endorser_gender_f * abs_strength_q1, data = df)
summary(model_rq3)
```

## Interpretation

- **$\beta_0$ (Intercept)**: Predicted initial trust for **male sponsors** when abs_strength = 0
- **$\beta_1$ (`endorser_gender_fWoman`)**: Baseline trust difference for female sponsors at zero strength
- **$\beta_2$ (`abs_strength_q1`)**: Slope for **male** sponsors — trust gained per unit of strength
- **$\beta_3$ (`endorser_gender_fWoman:abs_strength_q1`)**: **HQ3 test** — negative means females have a shallower slope

\newpage

## Visualization

```{r rq3-fig, fig.height=5, fig.cap="RQ3: Initial Trust by Sponsor Gender and Endorsement Strength"}
rq3_stats <- df %>%
  group_by(endorser_gender_f, strength_f) %>%
  summarise(
    mean_trust = mean(stake_percent_q1),
    se = sd(stake_percent_q1) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(rq3_stats,
       aes(x = strength_f, y = mean_trust, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_trust - se, ymax = mean_trust + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_trust, n)),
            position = position_dodge(0.8),
            vjust = 1.5, size = 4.5, color = "white", fontface = "bold") +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "RQ3: Do Female Sponsors Need Higher Strength to Achieve Same Trust?",
    subtitle = paste0("Mean Initial Trust (Decision 1) by Sponsor Gender and Endorsement Strength | N = ", nrow(df)),
    x = "Endorsement Strength Condition",
    y = "Initial Trust (%)",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 13)
  )
```

**Observed pattern:**

- At **Weak** endorsement strength, both genders start at similar initial trust (~48% for males, ~46% for females)
- At **Strong** endorsement strength, males receive **75.1%** trust vs. females at **62.1%** — a 13 pp gap
- The strong endorsement "boost" is **27.5 pp** for males but only **16.0 pp** for females
- The interaction is not significant (p = .229), but the direction is consistent with HQ3: female sponsors get less trust per unit of endorsement strength

\newpage

# RQ4: Trust Change by Gender $\times$ Strength $\times$ Outcome (3-Way Interaction)

**Hypothesis (HQ4)**: Trust change is **more** contingent on endorsement strength $\times$ outcome for female sponsors.

## Model

$$
\begin{aligned}
\text{trust\_change}_{i} = \beta_0 &+ \beta_1 \texttt{Woman}_{i} + \beta_2 \texttt{abs\_str\_q1\_c}_{i} + \beta_3 \texttt{Success}_{i} \\
&+ \beta_4 (\texttt{Woman} \times \texttt{abs\_str\_q1\_c})_{i} \\
&+ \beta_5 (\texttt{Woman} \times \texttt{Success})_{i} \\
&+ \beta_6 (\texttt{abs\_str\_q1\_c} \times \texttt{Success})_{i} \\
&+ \beta_7 (\texttt{Woman} \times \texttt{abs\_str\_q1\_c} \times \texttt{Success})_{i} \\
&+ \beta_8 \texttt{abs\_str\_q2\_c}_{i} + \epsilon_{i}
\end{aligned}
$$

```{r rq4-vars}
rq4_vars <- data.frame(
  Coefficient = c("Woman", "abs_str_q1_c", "Success", "3-way interaction", "abs_str_q2_c"),
  R_Name = c("endorser_gender_fWoman", "abs_strength_q1_c", "outcome_fSuccess",
             "...fWoman:abs_strength_q1_c:...fSuccess", "abs_strength_q2_c"),
  Coding = c("Man = 0 (ref), Woman = 1", "Mean-centered |Q1 slider - 50|",
             "Failure = 0 (ref), Success = 1", "Gender x Strength x Outcome",
             "Mean-centered |Q2 slider - 50|")
)
styled_kable(rq4_vars, col.names = c("Term", "Name in R output", "Coding"),
             row.names = FALSE)
```

- $\beta_7$ tests HQ4: positive $\beta_7$ means the strength $\times$ outcome interaction is **stronger** for female sponsors

```{r rq4-model, results='markup'}
model_rq4 <- lm(trust_change ~ endorser_gender_f * abs_strength_q1_c * outcome_f + abs_strength_q2_c,
                 data = df_tc)
summary(model_rq4)
```

## Interpretation

- **$\beta_3$ (`outcome_fSuccess`)**: The success boost for **male** sponsors at average endorsement strength
- **$\beta_5$ (`endorser_gender_fWoman:outcome_fSuccess`)**: How much smaller the success boost is for **female** sponsors (same as RQ1 but without the abs_strength control)
- **$\beta_6$ (`abs_strength_q1_c:outcome_fSuccess`)**: Whether stronger endorsements amplify the success boost for **males**
- **$\beta_7$ (3-way)**: **HQ4 test** — whether that amplification is different for **females**

\newpage

## Visualization

```{r rq4-fig, fig.height=6, fig.width=11, fig.cap="RQ4: Trust Change by Sponsor Gender, Endorsement Strength, and Outcome"}
rq4_stats <- df_tc %>%
  group_by(endorser_gender_f, strength_f, outcome_f) %>%
  summarise(
    mean_change = mean(trust_change),
    se = sd(trust_change) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(rq4_stats,
       aes(x = outcome_f, y = mean_change, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_change - se, ymax = mean_change + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_change, n),
                vjust = ifelse(mean_change >= 0, -0.5, 1.5)),
            position = position_dodge(0.8),
            size = 3.5, fontface = "bold", color = "black") +
  facet_wrap(~ strength_f, nrow = 1) +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(-55, 50), breaks = seq(-50, 50, 10)) +
  labs(
    title = "RQ4: Trust Change by Gender x Outcome, Moderated by Endorsement Strength",
    subtitle = paste0("Women rewarded MORE after weak endorsement success, LESS after strong | N = ", nrow(df_tc)),
    x = "Decision 1 Outcome",
    y = "Mean Change in Trust (%)",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    strip.text = element_text(size = 13, face = "bold"),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13)
  )
```

**Observed pattern:**

- The 3-way interaction is not significant (p = .877), indicating that the strength $\times$ outcome relationship does **not** meaningfully differ by sponsor gender
- **Male sponsors**: Success produces a ~20 pp trust boost regardless of whether the endorsement was weak or strong. After failure, strong-endorsed males are penalized more than weak-endorsed males
- **Female sponsors**: The success/failure distinction is essentially flat — all four bars hover near zero, with strong endorsements pulling slightly negative. Outcomes barely move trust change regardless of endorsement strength
- **Strong endorsements penalize both genders**: Across all conditions, strong endorsements are associated with *more negative* trust change than weak endorsements, consistent with the significant abs_strength_q1_c effect in RQ1
- The core gender asymmetry from RQ1 persists here — male sponsors' outcomes matter, female sponsors' outcomes do not — but this is not moderated by endorsement strength

\newpage

# Appendix: Robustness — Excluding Manipulation Check Failures

Participants were asked to identify the sponsor's gender after the task (Q44). Overall accuracy was `r round(mean(df$q44_resp == df$endorser_gender_code, na.rm = TRUE) * 100, 1)`%. Below we re-run the main analyses excluding participants who failed this check or did not respond.

```{r manip-filter, include=FALSE}
df_pass <- df %>% filter(q44_resp == endorser_gender_code)
df_pass_tc <- df_pass %>% filter(!is.na(trust_change)) %>%
  mutate(abs_strength_q1_c = abs_strength_q1 - mean(abs_strength_q1, na.rm = TRUE),
         abs_strength_q2_c = abs_strength_q2 - mean(abs_strength_q2, na.rm = TRUE))
```

```{r manip-summary}
cat("Manipulation check pass: N =", nrow(df_pass), "of", nrow(df), "\n")
cat("  Man:", sum(df_pass$endorser_gender_code == "Man"),
    "| Woman:", sum(df_pass$endorser_gender_code == "Woman"), "\n")
cat("  Excluded:", nrow(df) - nrow(df_pass),
    "(Man:", sum(df$endorser_gender_code == "Man") - sum(df_pass$endorser_gender_code == "Man"),
    "| Woman:", sum(df$endorser_gender_code == "Woman") - sum(df_pass$endorser_gender_code == "Woman"), ")\n")
```

## Appendix RQ1: Trust Change (Robustness)

```{r manip-rq1-model, results='markup'}
model_rq1_pass <- lm(trust_change ~ endorser_gender_f * outcome_f + abs_strength_q1_c + abs_strength_q2_c,
                      data = df_pass_tc)
summary(model_rq1_pass)
```

```{r manip-rq1-fig, fig.height=5.5, fig.cap="Appendix RQ1: Trust Change — Manipulation Check Passers Only"}
rq1_pass_stats <- df_pass_tc %>%
  group_by(endorser_gender_f, outcome_f) %>%
  summarise(
    mean_change = mean(trust_change),
    se = sd(trust_change) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(rq1_pass_stats,
       aes(x = outcome_f, y = mean_change, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_change - se, ymax = mean_change + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_change, n),
                vjust = ifelse(mean_change >= 0, -0.5, 1.5)),
            position = position_dodge(0.8),
            size = 4, fontface = "bold", color = "black") +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(-35, 25), breaks = seq(-30, 20, 10)) +
  labs(
    title = "Appendix RQ1: Excluding Manipulation Check Failures",
    subtitle = paste0("Trust Change | N = ", nrow(df_pass_tc), " (manipulation check passers only)"),
    x = "Decision 1 Outcome",
    y = "Mean Change in Trust (%)",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 13)
  )
```

\newpage

## Appendix RQ3: Initial Trust (Robustness)

```{r manip-rq3-model, results='markup'}
model_rq3_pass <- lm(stake_percent_q1 ~ endorser_gender_f * abs_strength_q1,
                      data = df_pass)
summary(model_rq3_pass)
```

```{r manip-rq3-fig, fig.height=5, fig.cap="Appendix RQ3: Initial Trust — Manipulation Check Passers Only"}
rq3_pass_stats <- df_pass %>%
  group_by(endorser_gender_f, strength_f) %>%
  summarise(
    mean_trust = mean(stake_percent_q1),
    se = sd(stake_percent_q1) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(rq3_pass_stats,
       aes(x = strength_f, y = mean_trust, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_trust - se, ymax = mean_trust + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_trust, n)),
            position = position_dodge(0.8),
            vjust = 1.5, size = 4.5, color = "white", fontface = "bold") +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "Appendix RQ3: Excluding Manipulation Check Failures",
    subtitle = paste0("Initial Trust | N = ", nrow(df_pass), " (manipulation check passers only)"),
    x = "Endorsement Strength Condition",
    y = "Initial Trust (%)",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 13)
  )
```

\newpage

## Appendix RQ4: Trust Change 3-Way (Robustness)

```{r manip-rq4-model, results='markup'}
model_rq4_pass <- lm(trust_change ~ endorser_gender_f * abs_strength_q1_c * outcome_f + abs_strength_q2_c,
                      data = df_pass_tc)
summary(model_rq4_pass)
```

```{r manip-rq4-fig, fig.height=6, fig.width=11, fig.cap="Appendix RQ4: Trust Change 3-Way — Manipulation Check Passers Only"}
rq4_pass_stats <- df_pass_tc %>%
  group_by(endorser_gender_f, strength_f, outcome_f) %>%
  summarise(
    mean_change = mean(trust_change),
    se = sd(trust_change) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

ggplot(rq4_pass_stats,
       aes(x = outcome_f, y = mean_change, fill = endorser_gender_f)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_change - se, ymax = mean_change + se),
                position = position_dodge(0.8), width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = sprintf("%.1f\n(n=%d)", mean_change, n),
                vjust = ifelse(mean_change >= 0, -0.5, 1.5)),
            position = position_dodge(0.8),
            size = 3.5, fontface = "bold", color = "black") +
  facet_wrap(~ strength_f, nrow = 1) +
  scale_fill_manual(values = c("Man" = PENN_BLUE, "Woman" = PENN_RED)) +
  scale_y_continuous(limits = c(-65, 55), breaks = seq(-60, 50, 10)) +
  labs(
    title = "Appendix RQ4: Trust Change 3-Way (Manipulation Check Passers)",
    subtitle = paste0("N = ", nrow(df_pass_tc), " (manipulation check passers only)"),
    x = "Decision 1 Outcome",
    y = "Mean Change in Trust (%)",
    fill = "Sponsor Gender"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11),
    strip.text = element_text(size = 13, face = "bold"),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13)
  )
```

\newpage

## Appendix Summary: Full Sample vs. Manipulation Check Passers

```{r manip-comparison}
# Use named coefficient indexing for robustness
rq1_int   <- "endorser_gender_fWoman:outcome_fSuccess"
rq3_int   <- "endorser_gender_fWoman:abs_strength_q1"
rq4_int   <- "endorser_gender_fWoman:abs_strength_q1_c:outcome_fSuccess"

comp <- data.frame(
  Test = c("RQ1: Gender x Outcome", "RQ3: Gender x Strength", "RQ4: 3-way"),
  Full_b = c(round(coef(model_rq1)[rq1_int], 2),
             round(coef(model_rq3)[rq3_int], 3),
             round(coef(model_rq4)[rq4_int], 3)),
  Full_p = c(round(summary(model_rq1)$coefficients[rq1_int, 4], 3),
             round(summary(model_rq3)$coefficients[rq3_int, 4], 3),
             round(summary(model_rq4)$coefficients[rq4_int, 4], 3)),
  Full_N = c(nrow(df_tc), nrow(df), nrow(df_tc)),
  Pass_b = c(round(coef(model_rq1_pass)[rq1_int], 2),
             round(coef(model_rq3_pass)[rq3_int], 3),
             round(coef(model_rq4_pass)[rq4_int], 3)),
  Pass_p = c(round(summary(model_rq1_pass)$coefficients[rq1_int, 4], 3),
             round(summary(model_rq3_pass)$coefficients[rq3_int, 4], 3),
             round(summary(model_rq4_pass)$coefficients[rq4_int, 4], 3)),
  Pass_N = c(nrow(df_pass_tc), nrow(df_pass), nrow(df_pass_tc))
)

styled_kable(comp,
             col.names = c("Interaction Test",
                           "b (Full)", "p (Full)", "N (Full)",
                           "b (Pass)", "p (Pass)", "N (Pass)"),
             align = "lcccccc",
             row.names = FALSE)
```
